---
title: "TITLE"
author: "AUTHORS"
includes:
  in_header:
    - \usepackage{lmodern}
output:
  pdf_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    toc: yes
  html_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    theme: journal
---


```{r}
library(igraph)
#library(dplyr)
#library(ggplot2)
library(gridExtra)
library(rgbif)
library(curl)
#library(tidyr)
library(jsonlite)
library(tidyverse)
library(taxize)
library(vegan)
library(randomForest)
library(gridExtra)
```

Let's start with querying WOL for plant-pollinator datasets. 


Querying the web of life API. 
Tutorial for how to do this found here: https://www.web-of-life.es/tutorial/session-download-data.html
```{r}
# define the base url
base_url <- "https://www.web-of-life.es/"   
json_url2 <- paste0(base_url,"get_networks.php?interaction_type=Pollination") 

WolPols <- jsonlite::fromJSON(json_url2)
WolMeta <- read.csv(paste0(base_url,"get_network_info.php")) %>%dplyr::filter(., network_type%in%"Pollination")
length(unique(WolPols$network_name)) # 174 Networks

WolMeta <- read.csv(paste0(base_url,"get_network_info.php"))
WolMeta <- WolMeta %>% dplyr::filter(., network_type%in%"Pollination") #Make sure we have only pollination
WolMeta <- WolMeta %>% 
  #dplyr::select(., network_name, region, latitude, longitude) %>% 
  left_join(WolPols, ., by="network_name")
#WolMeta <- dplyr::select(WolMeta, -Taxa.y) %>% dplyr::rename(., Taxa=Taxa.x)
```

Let's do some double checking to 
1) Separate vertebrate from invertebrate pollination networks
%2) Make different sources are correctly harmonized #Turns out these are the new deal

I was first going check every taxa with taxize, but turns out this actually takes a long time to run with so many taxa. Instead, I looked at the original papers for the 74 publications included in these data. Slow, but still faster than taxize. I load in the key I created for that below. 

```{r}
studykey <- read.csv(file="studykey.csv")
WolMeta <- left_join(WolMeta, studykey, by=c("author", "reference"))

WolMeta<- dplyr::filter(WolMeta, grepl("Unidentified", species2, ignore.case=F)==F) #remove unidentified
WolMeta<- dplyr::filter(WolMeta, grepl(" sp[1-9]+", species2, ignore.case=F)==F) #remove those with polls identified to genera only
WolMeta<- dplyr::filter(WolMeta, grepl(" sp[1-9]+", species1, ignore.case=F)==F) #remove those plants identified to genera only
#Interesting to evaluate whether to do this on a local level, but necessary with global metaweb (sp1 in one network may be sp2 in another, etc)

mixedwebs <- dplyr::filter(WolMeta, Taxa=="Mixed")
Insectweb <- dplyr::filter(WolMeta, Taxa=="Insecta")
Birdweb <- dplyr::filter(WolMeta, Taxa=="Aves")

Insectweb <- dplyr::filter(mixedwebs, grepl(c("Apis"), species2)==T | grepl(c("Ornidia"), species2)==T | grepl(c("Bombus"), species2)==T | grepl(c("Musca"), species2)==T ) %>% rbind(Insectweb, .) #Add in some common insect genera from mixed webs

mixedwebs <- dplyr::filter(mixedwebs, grepl(c("Apis"), species2)==F & grepl(c("Ornidia"), species2)==F & grepl(c("Bombus"), species2)==F & grepl(c("Musca"), species2)==F ) #Remove these from the to-query group


mixedord <- tax_name(unique(mixedwebs$species2), get = "class", db = "ncbi")

missing <- dplyr::filter(mixedord, is.na(class)==T)
missing$query[missing$query=="Politmus milleri"] <- "Polytmus milleri" #Mispelled bird
missing$query[missing$query=="Physiphoa azurea"] <- "Physiphora azurea " #Mispelled fly

missing$gen <- gsub( " .*$", "", missing$query) 
gens <- data.frame(gen=missing$gen, class=NA) %>% unique()
gens <- dplyr::filter(gens, gen %in% c("Clamirius", "Eurymetopun")==F) #Can't find these

gens$class[gens$gen%in%c("Amazilia", "Carduelis", "Foudia", "Polytmus")] <- "Aves" #The birds in the list
gens$class[is.na(gens$class)==T] <- "Insect" #Everything left is an insect 

missing <- missing %>% dplyr::select(., -class) %>% left_join(., gens, by="gen") %>% na.omit() #Grab the missing classes

Birdweb  <- dplyr::filter(mixedwebs, species2 %in% missing$query[missing$class=="Aves"]) %>%
  rbind(Birdweb,.)
Insectweb <- dplyr::filter(mixedwebs, species2 %in% missing$query[missing$class=="Insecta"]) %>%
  rbind(Insectweb,.)
```
Some preliminary network stats
```{r}
 WolMeta %>%
  group_by(latitude, longitude) %>%
  summarise(site_index = cur_group_id()) %>%
  ungroup()
 
length(c(unique(WolMeta$species1), unique(WolMeta$species2)))
```



Now that we've done our filtering, let's check out our two created metawebs
```{r, eval=F}
InsectMeta <- dplyr::select(Insectweb, species1, species2) %>% unique()
imeta <- igraph::graph_from_data_frame(InsectMeta, directed=F) #Create igraph object


BirdMeta <- dplyr::select(Birdweb, species1, species2) %>% unique()
bmeta <- igraph::graph_from_data_frame(BirdMeta, directed=F) #Create igraph object
save(InsectMeta, imeta, BirdMeta, bmeta, file="data/metawebs.RDA")
save(Birdweb, Insectweb, file="data/Parallelwebs.RDA")
```

Load in the data from above so we don't have to repeat our query
```{r}
load("data/metawebs.RDA")
```


Need to remove species not located in the main component of the metaweb (otherwise can't compute centrality)
```{r}
V(imeta)$component <- components(imeta)$membership
components(imeta)$csize #Largest component has 6237 nodes; the rest are isolated pairs
imeta <- delete.vertices(imeta, V(imeta)$component!=which.max(components(imeta)$csize)) #Remove vertices that aren't included in the largest component
table(V(imeta)$component)



V(bmeta)$component <- components(bmeta)$membership
components(bmeta)$csize #Largest component has 721 nodes; the rest are isolated pairs
bmeta <- delete.vertices(bmeta, V(bmeta)$component!=which.max(components(bmeta)$csize)) #Remove vertices that aren't included in the largest component
table(V(bmeta)$component)
```


Let's calculate our measures of species centrality in the metaweb

```{r}
imetaCent <- data.frame(between=igraph::centralization.betweenness(imeta)$res,
           close=igraph::centralization.closeness(imeta)$res,
           deg=igraph::centralization.degree(imeta, mode="all")$res,
           eig=igraph::centralization.evcent(imeta)$vector,
           node=V(imeta)$name)

bmetaCent <- data.frame(between=igraph::centralization.betweenness(bmeta)$res,
           close=igraph::centralization.closeness(bmeta)$res,
           deg=igraph::centralization.degree(bmeta, mode="all")$res,
           eig=igraph::centralization.evcent(bmeta)$vector,
           node=V(bmeta)$name)

## Use n equally spaced breaks to assign each value to n-1 equal sized bins 
ii <- cut(bmetaCent$close, breaks = seq(min(bmetaCent$close, na.rm=T), max(bmetaCent$close, na.rm=T), len = 50), 
          include.lowest = TRUE)

## Use bin indices, ii, to select color from vector of n-1 equally spaced colors
V(bmeta)$color <- colorRampPalette(c("lightblue", "blue"))(50)[ii]
```


Making a map plot we can use
```{r}
maps::map('world', fill = TRUE, col = "white")
points(x=WolMeta$longitude, y=WolMeta$latitude)
``` 



Plots for the conceptual figure
```{r}
#Bird Metaweb
set.seed(7)
lay1 <- layout_nicely(bmeta)
#pdf(file="figs/bmeta_fig.pdf", width=12, height=12)
plot(bmeta, vertex.label=NA, layout=lay1, vertex.size=2, vertex.cex=2, frame.color=NA)
#dev.off()
```

```{r}

colored_subplot <- function(networknm, flnm, vertcol){
  bsub <- dplyr::filter(Birdweb, network_name=="M_PL_069_01") %>% dplyr::select(., species1, species2) %>% unique()
  bsub <- igraph::graph_from_data_frame(bsub, directed=F) #Create idgraph object
  V(bsub)$component <- components(bsub)$membership
  bsub <- delete.vertices(bsub, V(bsub)$component!=which.max(components(bsub)$csize)) #Remove vertices that aren't included in the largest component
  
  bmsub1Cent <- data.frame(between=igraph::centralization.betweenness(bsub)$res,
             close=igraph::centralization.closeness(bsub)$res,
             node=V(bsub)$name)
  
  ## Use n equally spaced breaks to assign each value to n-1 equal sized bins 
  ii <- cut(bmsub1Cent$close, breaks = seq(min(bmsub1Cent$close, na.rm=T), max(bmsub1Cent$close, na.rm=T), len = 10), 
            include.lowest = TRUE)
  
  ## Use bin indices, ii, to select color from vector of n-1 equally spaced colors
  V(bsub)$color <- colorRampPalette(c("lightblue", "blue"))(10)[ii]
  lay <- layout_nicely(bsub)
  
  pdf(file=flnm, width=12, height=12)
  plot(bsub, vertex.label=NA, layout=lay, vertex.size=15, vertex.color=vertcol)
  plot(bsub, vertex.label=NA, layout=lay, vertex.size=11, add=T)
  dev.off()
  
  bmsub1Cent$col <- vertcol
  return(bmsub1Cent)
}

table(Birdweb$network_name)
sub1 <- colored_subplot(networknm="M_PL_069_01", flnm="figs/subplot1.pdf", vertcol="red")
sub2 <- colored_subplot(networknm="M_PL_064", flnm="figs/subplot2.pdf", vertcol="orange")
```


```{r}
V(bmeta)$altcol <- NA
V(bmeta)$altcol[V(bmeta)$name %in% sub1$node] <- "red"
V(bmeta)$altcol[V(bmeta)$name %in% sub2$node] <- "orange"

#pdf(file="figs/bmeta_fig2.pdf", width=12, height=12)
plot(bmeta, vertex.label=NA, layout=lay1, vertex.size=3, vertex.color=V(bmeta)$altcol, edge.color=NA)
plot(bmeta, vertex.label=NA, layout=lay1, vertex.size=2, frame.color=NA, add=T)
#dev.off()

```


For the few plant species present in both insect and bird networks, is their centrality similiar in both networks? In short: No
```{r}
overlaps <- dplyr::filter(bmetaCent, node %in% imetaCent$node)

overlaps <- imetaCent %>% dplyr::select(node, deg, eig, close) %>% dplyr::rename(., insect_deg=deg, insect_eig=eig, insect_close=close) %>% left_join(overlaps, ., by="node")

plot(overlaps$eig, overlaps$insect_eig, xlab="Eigenvalue Centrality in Bird Network", ylab="Eigenvalue Centrality in Insect Network")
cor.test(overlaps$eig, overlaps$insect_eig)
plot(overlaps$deg, overlaps$insect_deg, xlab="Degree in Bird Network", ylab="Degree in Insect Network")
cor.test(overlaps$deg, overlaps$insect_deg)

plot(overlaps$close, overlaps$insect_close, xlab="Closeness in Bird Network", ylab="Closeness in Insect Network")
cor.test(overlaps$close, overlaps$insect_close)
```


```{r}
sp <- unique(imetaCent$node, bmetaCent$node)
length(sp)
```

Let's actually look at geographic ranges
```{r}
georng <- read.csv(file="data/geosummaryout.csv") 
envrng <- read.csv(file="data/envsummaryout.csv")
```

Add envriornmental range to our existing data
```{r}
envrng$node <- envrng$file
envrng$node <- gsub("_", " ", envrng$node)
envrng$node <- gsub(".csv", "", envrng$node)
envrng$node <- paste(toupper(substring(envrng$node, 1, 1)), substring(envrng$node, 2), sep="")

imetaCent <- dplyr::select(envrng, envarea, node) %>% left_join(imetaCent, ., by="node")
bmetaCent <- dplyr::select(envrng, envarea, node) %>% left_join(bmetaCent, ., by="node")
```

Add geographic range size to the data quality
```{r}
colnames(georng)
globgeo <- georng %>% 
  dplyr::group_by(., file) %>% 
  dplyr::summarise(., globkm=sum(contgeokm.area))

globgeo$node <- globgeo$file
globgeo$node <- gsub("_", " ", globgeo$node)
globgeo$node <- gsub(".csv", "", globgeo$node)
globgeo$node <- paste(toupper(substring(globgeo$node, 1, 1)), substring(globgeo$node, 2), sep="") 
globgeo <- dplyr::select(globgeo, -file)

imetaCent <- left_join(imetaCent, globgeo, by="node")
bmetaCent <- left_join(bmetaCent, globgeo, by="node")
```


Add a columns so we can separate our taxa if we desire
```{r}
imetaCent$type <- NA
imetaCent$type[imetaCent$node %in% InsectMeta$species1] <- "Plant"
imetaCent$type[imetaCent$node %in% InsectMeta$species2] <- "Insect"

bmetaCent$type <- NA
bmetaCent$type[bmetaCent$node %in% BirdMeta$species1] <- "Plant"
bmetaCent$type[bmetaCent$node %in% BirdMeta$species2] <- "Bird"

hist(imetaCent$eig)
hist(imetaCent$close)
```

Investigative plotting of relationship between envrionmental range and centrality

```{r}
imetaCent %>% #dplyr::filter(., close<0.5) %>% 
  ggplot(., aes(x=scale(log(envarea)), y=close, col=type))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~type)+
  theme_classic()+
  xlab("Scaled Log Enviornmental Area")+
  ylab("Closeness Centrality")


bmetaCent %>% dplyr::filter(., close<0.5) %>% 
  ggplot(., aes(x=scale(log(envarea)), y=close, col=type))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~type)+
  theme_classic()+
  xlab("Scaled Log Enviornmental Area")+
  ylab("Closeness Centrality")

hist(scale(log(imetaCent$envarea)))
```

Prediction: A linear model approach
```{r}
imetaCentmodat <- imetaCent
imetaCentmodat <- dplyr::filter(imetaCentmodat, close<0.5) #Filter out outliers

inmod <- lm(close~scale(log(envarea))+as.factor(type)+scale(log(globkm)), data=imetaCentmodat)

inmod <- lm(close~scale(log(envarea))+scale(log(globkm))+scale(log(globkm))*as.factor(type), data=imetaCentmodat)
summary(inmod)
car::vif(inmod)


inmod2 <- lm(close~scale(log(envarea))+as.factor(type), data=imetaCentmodat)

plot(inmod)
summary(inmod)

#inmod <- lm(close~scale(log(envarea))+scale(log(globkm))+scale(log(envarea))|as.factor(type)+scale(log(globkm))|as.factor(type), data=imetaCentmodat)

#plot(inmod)
#summary(inmod)


cor.test(scale(log(imetaCentmodat$envarea)), scale(log(imetaCentmodat$globkm)))
car::vif(inmod)

bmetaCentmodat <- bmetaCent
bmetaCentmodat <- dplyr::filter(bmetaCentmodat, close<0.5)
#bmod <- lm(close~scale(log(envarea))+as.factor(type)+as.factor(type)*scale(log(envarea))+scale(log(globkm))+as.factor(type)*scale(log(globkm)), data=bmetaCentmodat)
bmod <- lm(close~scale(log(envarea))+as.factor(type)+scale(log(globkm)), data=bmetaCentmodat)
summary(bmod)
summary(inmod)
plot(bmod)

cor.test(scale(log(bmetaCentmodat$envarea)), scale(log(bmetaCentmodat$globkm)))
car::vif(bmod)

cor.test(imetaCentmodat$envarea, imetaCentmodat$globkm)
  
  
inmod <- lm(close~scale(log(envarea))+as.factor(type)+scale(log(globkm)), data=imetaCentmodat)

#inmod <- lm(close~scale(log(envarea))+as.factor(type)+scale(log(globkm))+scale(log(globkm))*scale(log(envarea)), data=imetaCentmodat)

summary(inmod)
summary(bmod)
car::vif(inmod)

bmetaCentmodat
```

```{r}
imetaCent %>% dplyr::filter(., close<0.5) %>% 
  ggplot(., aes(x=scale(log(globkm)), y=close, col=type))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~type)+
  theme_classic()+
  xlab("Scaled Geographic Area")+
  ylab("Closeness Centrality")


bmetaCent %>% dplyr::filter(., close<0.5) %>% 
  ggplot(., aes(x=scale(log(globkm)), y=close, col=type))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~type)+
  theme_classic()+
  xlab("Scaled Geographic Area")+
  ylab("Closeness Centrality")
```
Let's make some slightly prettier plots for this

```{r}
imetaCent$net <- "Insect"
bmetaCent$net <- "Bird"
composite <- rbind(dplyr::select(imetaCent, envarea, globkm, node, type, net, close), dplyr::select(bmetaCent, envarea, globkm, node, type, net, close)) %>% dplyr::filter(., is.na(envarea)==F)

unique(composite$type)

composite$type[composite$type %in% c("Insect", "Bird")] <- "Floral Visitor"

geop1 <- composite %>% dplyr::filter(., close<0.5) %>% 
  ggplot(., aes(x=scale(log(globkm)), y=close, col=net))+
  geom_point(alpha=0.5)+
  geom_smooth(method="lm")+
  facet_wrap(~type, labeller = labeller(type = c("Floral Visitors", "Plants")))+
  theme_classic()+
  xlab("Scaled Log Geographic Area")+
  ylab("Closeness Centrality")+guides(col=guide_legend(title="MetaNetwork"))+
  scale_color_manual(labels = c("Avian-Plant", "Insect-Plant"), values = c("#0F882C", "dodgerblue"))+
  theme(legend.position=c(0.11,.81), guide_legend(override.aes=list(fill=NA)))

envp1 <- composite %>% dplyr::filter(., close<0.5) %>% 
  ggplot(., aes(x=scale(log(envarea)), y=close, col=net))+
  geom_point(alpha=0.5)+
  geom_smooth(method="lm")+
  facet_wrap(~type)+
  theme_classic()+
  xlab("Scaled Log Environmental Area")+
  ylab("Closeness Centrality")+guides(col="none")+
  scale_color_manual(labels = c("Avian-Plant", "Insect-Plant"), values = c("#0F882C", "dodgerblue"))
```

Fig at the metaweb level
```{r}
#pdf(file="figs/metaweb_area_scaling.pdf", width=6, height=6)
grid.arrange(geop1, envp1, nrow=2)
#dev.off()

summary(inmod)
```

envp1

Some of the networks with different IDs actually are sampled at the same site (potentially from different years, etc). I'd like to combine each of these into site-specific rather than study specific, so I add a siteindex here below. 
```{r}
Birdweb <- Birdweb %>%
  group_by(latitude, longitude) %>%
  mutate(site_index = cur_group_id()) %>%
  ungroup()

length(unique(Birdweb$network_name))
length(unique(Birdweb$site_index))


Insectweb <- Insectweb %>%
  group_by(latitude, longitude) %>%
  mutate(site_index = cur_group_id()) %>%
  ungroup()

length(unique(Insectweb$network_name))
length(unique(Insectweb$site_index))
length(unique(Birdweb$site_index))
```
 
 
Adding in our z-transformed global stuff 
```{r}
load(file="BmetawebSwaps_raw.Rda")
load(file="ImetawebSwaps_raw.Rda")


isums <- dplyr::group_by(imetaCent_null, node) %>%
  dplyr::summarise(., meancl=mean(close), sdcl=sd(close))

imetaCent <- left_join(imetaCent,isums, by="node")
imetaCent$close.z <- (imetaCent$close-imetaCent$meancl)/imetaCent$sdcl

imetaCent %>% 
  ggplot(., aes(x=scale(log(globkm)), y=close.z, col=type))+
  geom_point(alpha=0.1)+
  geom_smooth(method="lm")+
  facet_wrap(~type)+
  theme_classic()+
  xlab("Scaled Geographic Area")+
  ylab("Z-transformed Closeness Centrality")

imetaCent %>% 
  ggplot(., aes(x=scale(log(envarea)), y=close.z, col=type))+
  geom_point(alpha=0.1)+
  geom_smooth(method="lm")+
  facet_wrap(~type)+
  theme_classic()+
  xlab("Scaled Environmental Area")+
  ylab("Z-transformed Closeness Centrality")

fam <-  dplyr::filter(imetaCent, type=="Plant") %>% 
lm(data=., formula = close.z~scale(log(envarea)))
summary(fam)

fam <-  dplyr::filter(imetaCent, type=="Plant") %>% 
lm(data=., formula = close.z~scale(log(globkm)))
summary(fam)
```
 
 
 Let's calculate centrality on a local level for each node of the networks that make up our metawebs. 
 
 This takes a while, so I'm setting default=F and loading outputs below. 
```{r, eval=F}

localiCent <- NULL
for(i in 1:length(unique(Insectweb$site_index))){
    temp <- Insectweb[Insectweb$site_index==i,]
      if(nrow(temp)<4){ #if too small a network, skip it
      next
    }
    
    temp <- dplyr::select(temp, species1, species2) %>% unique() #grab unique interactions
    tmeta <- igraph::graph_from_data_frame(temp, directed=F) #Create igraph object
    tbig <- igraph::graph_from_incidence_matrix(table(temp)) #Create a large network where we don't do component drop (for null model later)
    
    V(tmeta)$component <- components(tmeta)$membership #Assign component membership
    tmeta <- igraph::delete.vertices(tmeta, V(tmeta)$component!=which.max(components(tmeta)$csize)) #Remove vertices that aren't included in the largest component
    
    tmetaCent <- data.frame(between=igraph::centralization.betweenness(tmeta)$res, #Calculate our centrality measures (locally)
               close=igraph::centralization.closeness(tmeta)$res,
               deg=igraph::centralization.degree(tmeta, mode="all")$res,
               eig=igraph::centralization.evcent(tmeta)$vector,
               node=V(tmeta)$name,
               site_index=i)
    #Now we have our actual metric, but we need a null model approach
    ## Perform z-score standardization
    rndout <- NULL
    nullsetup <- nullmodel(table(temp), method = "quasiswap")
    out <- simulate(nullsetup, nsim=1000) #Set up our null model object (see vegan vignette)
    for(simID in 1:1000){
      rg <- igraph::graph_from_incidence_matrix(out[,,simID])
      V(rg)$component <- components(rg)$membership #Assign component membership
      rg <- delete.vertices(rg, V(rg)$component!=which.max(components(rg)$csize)) #Remove vertices that aren't included in the largest component    
      rgCent <- data.frame(between=igraph::centralization.betweenness(rg)$res,
                   close=igraph::centralization.closeness(rg)$res,
                   deg=igraph::centralization.degree(rg, mode="all")$res,
                   eig=igraph::centralization.evcent(rg)$vector,
                   site_index=i, #Grab the site
                   sim=simID,
                   node=V(rg)$name) #Which simulation is this
      rndout <- rbind(rgCent, rndout)
    }
    #Calculate the z-score
    tmetaCent$z.close <- NA
    for(j in 1:nrow(tmetaCent)){ #Perform ranking for each node
      ret <- dplyr::filter(rndout, node==tmetaCent$node[j]) #Find all of the simulated values for a given node
      emp <- dplyr::filter(tmetaCent, node==tmetaCent$node[j]) #Grab the empirical value
      #tmetaCent$z.close[tmetaCent$node==ret$node[j]] <-sum(emp$close>ret$close)/length(ret$close) #assign a z-score based on empirical value ranking; old version
      tmetaCent$z.close[tmetaCent$node==ret$node[j]] <- (emp$close - mean(ret$close, na.rm=TRUE))/sd(ret$close, na.rm=TRUE) #Updated; z-score based on normality
    localiCent <- rbind(localiCent, tmetaCent)
  }
}




localbCent <- NULL
for(i in 1:length(unique(Birdweb$site_index))){ #Iterate over each local network
  temp <- Birdweb[Birdweb$site_index==i,]
    if(nrow(temp)<4){ #if too small a network, skip it
    next
  }
  
  temp <- dplyr::select(temp, species1, species2) %>% unique() #grab unique interactions
  tmeta <- igraph::graph_from_data_frame(temp, directed=F) #Create igraph object
  
  V(tmeta)$component <- components(tmeta)$membership #Assign component membership
  tmeta <- delete.vertices(tmeta, V(tmeta)$component!=which.max(components(tmeta)$csize)) #Remove vertices that aren't included in the largest component
  
  #Calculate centrality metrics (raw)
  tmetaCent <- data.frame(between=igraph::centralization.betweenness(tmeta)$res, 
             close=igraph::centralization.closeness(tmeta)$res,
             deg=igraph::centralization.degree(tmeta, mode="all")$res,
             eig=igraph::centralization.evcent(tmeta)$vector,
             node=V(tmeta)$name,
             site_index=i)
  
  ## Perform z-score standardization
  rndout <- NULL
  nullsetup <- nullmodel(table(temp), method = "quasiswap")
  out <- simulate(nullsetup, nsim=1000) #Set up our null model object (see vegan vignette)
  for(simID in 1:1000){
    rg <- igraph::graph_from_incidence_matrix(out[,,simID])
    V(rg)$component <- components(rg)$membership #Assign component membership
    rg <- delete.vertices(rg, V(rg)$component!=which.max(components(rg)$csize)) #Remove vertices that aren't included in the largest component    
    rgCent <- data.frame(between=igraph::centralization.betweenness(rg)$res,
                 close=igraph::centralization.closeness(rg)$res,
                 deg=igraph::centralization.degree(rg, mode="all")$res,
                 eig=igraph::centralization.evcent(rg)$vector,
                 site_index=i, #Grab the site
                 sim=simID,
                 node=V(rg)$name) #Which simulation is this
    rndout <- rbind(rgCent, rndout)
  }
  #Calculate the z-score
  tmetaCent$z.close <- NA
  for(j in 1:nrow(tmetaCent)){ #Perform ranking for each node
    ret <- dplyr::filter(rndout, node==tmetaCent$node[j]) #Find all of the simulated values for a given node
    emp <- dplyr::filter(tmetaCent, node==tmetaCent$node[j]) #Grab the empirical value
    #tmetaCent$z.close[tmetaCent$node==ret$node[j]] <-sum(emp$close>ret$close)/length(ret$close) #Previous version based on ranking assign a z-score based on empirical value
    tmetaCent$z.close[tmetaCent$node==ret$node[j]] <- (emp$close - mean(ret$close))/sd(ret$close) #Updated; z-score based on normality
    tmetaCent$z.close.sd <- sd(ret$close)
  }
  #Save our local metric to the larger dataset
  localbCent <- rbind(localbCent, tmetaCent)
}

length(unique(rndout$node))

save(localbCent, localiCent, file="data/z_localCent_Zupdated.RDA")
```

Analyzing the output of our z-transformation of local centrality measures. 
```{r}
load(file="data/z_localCent_Zupdated.RDA")
#load(file="data/z_localCent.RDA")


localiz <-localiCent %>% #Take the summary output
  group_by(., node) %>% #grab for each node
  dplyr::summarise(., nsites=length(unique(site_index)), localmeanclose=mean(close), localmeanclose.z=mean(z.close, na.rm=T)) %>% #Find mean of each nodes average local centralities, both z-tranformed and not
  ungroup()

imetaCent <- dplyr::left_join(imetaCent, localiz, by="node") #Add local  measure back to metaWeb version

imetaCent %>% ggplot(., aes(x=localmeanclose,y=close, col=log(nsites)))+
  geom_point()+
  xlab("Mean Local Closeness")+
  ylab("Global Closeness")+theme_classic()

imetaCent %>% ggplot(., aes(x=localmeanclose.z,y=localmeanclose, col=log(nsites)))+
  geom_point()+
  xlab("Mean Local Closeness (Z-transformed)")+
  ylab("Mean Local Closeness (Non-transformed)")+theme_classic()


localbz <-localbCent %>% #Take the summary output
  group_by(., node) %>% #grab for each node
  dplyr::summarise(., nsites=length(unique(site_index)), localmeanclose=mean(close), localmeanclose.z=mean(z.close, na.rm=T)) %>% #Find mean of each nodes average local centralities, both z-tranformed and not
  ungroup()

bmetaCent <- dplyr::left_join(bmetaCent, localbz, by="node") #Add local  measure back to metaWeb version

bmetaCent %>% ggplot(., aes(x=localmeanclose,y=close, col=log(nsites)))+
  geom_point()+
  xlab("Mean Local Closeness")+
  ylab("Global Closeness")+theme_classic()

bmetaCent %>% ggplot(., aes(x=localmeanclose.z,y=localmeanclose, col=log(nsites)))+
  geom_point()+
  xlab("Mean Local Closeness (Z-transformed)")+
  ylab("Mean Local Closeness (Non-transformed)")+theme_classic()

```

## Variability across local sites
Let's look at the variance of the species with the most different observations in local networks. 
First, we'll just plot the raw centrality metrics
```{r}
ireps <-localiCent[localiCent$node%in%dplyr::filter(localiz, nsites>9)$node,] %>% #Just grab replicates from species
  group_by(., node, site_index) %>% #group by species and site (since we're interested in variance across sites)
  dplyr::summarise(., localmeanclose=mean(close), localmeanclose.z=mean(z.close, na.rm=T)) %>% #Find mean of each nodes average local centralities, both z-tranformed and not
  ungroup() %>% 
  left_join(., dplyr::select(localiz, node, nsites), by="node") %>%
  ungroup()

breps <-localbCent[localbCent$node%in%dplyr::filter(localbz, nsites>6)$node,] %>% #Just grab replicates from species
  group_by(., node, site_index) %>% #group by species and site (since we're interested in variance across sites)
  dplyr::summarise(., localmeanclose=mean(close), localmeanclose.z=mean(z.close, na.rm=T)) %>% #Find mean of each nodes average local centralities, both z-tranformed and not
  ungroup() %>% 
  left_join(., dplyr::select(localbz, node, nsites), by="node") %>%
  ungroup()

breps <- dplyr::select(bmetaCent, node, close) %>% unique() %>% left_join(breps, ., by="node")
ireps <- dplyr::select(imetaCent, node, close) %>% unique() %>% left_join(ireps, ., by="node")

brep <- ggplot(aes(x=factor(node, levels=unique(node[order(nsites, decreasing = T)])), y=localmeanclose,
           fill=nsites), data=breps)+
  geom_boxplot(outlier.shape = NA)+ 
  scale_fill_continuous(name = "Number of Sites")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 305, vjust = 0.5, hjust=0))+
  ylab("Local Closeness")+
  xlab("Species")+
  geom_point(aes(x=factor(node, levels=unique(node[order(nsites, decreasing = T)])), y=localmeanclose), size=1.5)+
  geom_point(aes(x=factor(node, levels=unique(node[order(nsites, decreasing = T)])), y=close), col="red")+ylim(0,1)

irep <- ggplot(aes(x=factor(node, levels=unique(node[order(nsites, decreasing = T)])), y=localmeanclose,
           fill=log(nsites)), data=ireps)+
  geom_boxplot(outlier.shape = NA)+ 
  scale_fill_continuous(name = "Log Number of Sites")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 305, vjust = 0.5, hjust=0))+
  ylab("Local Closeness")+
  xlab("Species")+
  geom_point(aes(x=factor(node, levels=unique(node[order(nsites, decreasing = T)])), y=localmeanclose), size=0.5)+
  geom_point(aes(x=factor(node, levels=unique(node[order(nsites, decreasing = T)])), y=close), col="red")+
  theme(axis.text.x=element_text(size=6))+ylim(0,1)
```


Now let's do the same with the standardized metrics.

```{r}
brep.z <- ggplot(aes(x=factor(node, levels=unique(node[order(nsites, decreasing = T)])), y=localmeanclose.z,
           fill=nsites), data=breps)+
  geom_boxplot(outlier.shape = NA)+ 
  scale_fill_continuous(name = "Number of Sites")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 305, vjust = 0.5, hjust=0))+
  ylab("Local Closeness (Z-transformed)")+
  xlab("Species")+
  geom_point(aes(x=factor(node, levels=unique(node[order(nsites, decreasing = T)])), y=localmeanclose.z), size=1.5)+
  geom_hline(yintercept=1.96, color="red", lty=2)+
  geom_hline(yintercept=-1.96, color="red", lty=2)
  #+ylim(0,1)

irep.z <- ggplot(aes(x=factor(node, levels=unique(node[order(nsites, decreasing = T)])), y=localmeanclose.z,
           fill=log(nsites)), data=ireps)+
  geom_boxplot(outlier.shape = NA)+ 
  scale_fill_continuous(name = "Log Number of Sites")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 305, vjust = 0.5, hjust=0))+
  ylab("Local Closeness (Z-transformed)")+
  xlab("Species")+
  geom_point(aes(x=factor(node, levels=unique(node[order(nsites, decreasing = T)])), y=localmeanclose.z), size=0.5)+
  theme(axis.text.x=element_text(size=6))+
  geom_hline(yintercept=1.96, color="red", lty=2)+
  geom_hline(yintercept=-1.96, color="red", lty=2)
```
Plotting variation of local centrality
```{r}
#pdf(file="figs/localCentralityVariation_z.trans.pdf", width=11, height=8.5)
grid.arrange(brep, brep.z, irep, irep.z, nrow=2)
#dev.off()
```

Effects of range size on mean local centralirt

```{r}
composite_local <- rbind(imetaCent, bmetaCent)

geop1_local <- composite_local %>% #dplyr::filter(., close<0.5) %>% 
  ggplot(., aes(x=scale(log(globkm)), y=localmeanclose.z, col=net))+
  geom_point(alpha=0.5)+
  geom_smooth(method="lm")+
  facet_wrap(~type)+
  theme_classic()+
  xlab("Scaled Log Environmental Area")+
  ylab("Mean Z-Transformed Local Closeness")+guides(col="none")+
  scale_color_manual(labels = c("Avian-Plant", "Insect-Plant"), values = c("#0F882C", "dodgerblue"))

envp1_local <- composite_local %>% #dplyr::filter(., close<0.5) %>% 
  ggplot(., aes(x=scale(log(envarea)), y=localmeanclose.z, col=net))+
  geom_point(alpha=0.5)+
  geom_smooth(method="lm")+
  facet_wrap(~type)+
  theme_classic()+
  xlab("Scaled Log Environmental Area")+
  ylab("Mean Z-Transformed Local Closeness")+guides(col="none")+
  scale_color_manual(labels = c("Avian-Plant", "Insect-Plant"), values = c("#0F882C", "dodgerblue"))
```


Fig of the effect of local centrality 
```{r}
#pdf(file="figs/metaweb_area_scaling_local.pdf", width=6, height=6)
grid.arrange(geop1_local, envp1_local, nrow=2)
#dev.off()
```



```{r}
imetaCentmodat <- imetaCent
imetaCentmodat <- dplyr::filter(imetaCentmodat, close<0.5) #Filter out outliers
inmod.z <- glm(localmeanclose.z
~scale(log(envarea))+as.factor(type)+scale(log(globkm)), data=imetaCentmodat)
plot(inmod.z)
summary(inmod.z)

cor.test(scale(log(imetaCentmodat$envarea)), scale(log(imetaCentmodat$globkm)))
 car::vif(inmod.z)

bmetaCentmodat <- bmetaCent
bmetaCentmodat <- dplyr::filter(bmetaCentmodat, close<0.5)
#bmod <- lm(close~scale(log(envarea))+as.factor(type)+as.factor(type)*scale(log(envarea))+scale(log(globkm))+as.factor(type)*scale(log(globkm)), data=bmetaCentmodat)
bmod.z <- glm(localmeanclose.z~scale(log(envarea))+as.factor(type)+scale(log(globkm)), data=bmetaCentmodat)
summary(bmod.z)
plot(bmod.z)

cor.test(scale(log(bmetaCentmodat$envarea)), scale(log(bmetaCentmodat$globkm)))
car::vif(bmod.z)
```

Finally, let's actually do a z-standardization of the global metaweb based on shuffling individual composite webs and then combining them. This takes a long time, so I rewrote it in `Parallel_MetawebSwaps.R` to run it remotely. 

```{r, eval=FALSE}
Vset <- NULL
Eset <- NULL
bmetaCent_null <- NULL
nsim <- 3
for(i in 1:nsim){ #Iterate over each local network
  for(j in 1:length(unique(Birdweb$site_index))){ #Reshuffle on each local network
    print(paste(j, "loaded", sep=" "))
  temp <- Birdweb[Birdweb$site_index==j,] #grab the local web
  if(nrow(temp)<3){ #If there's less than 3 nodes skip it
    print("too few")
    next
  }
  temp <- dplyr::select(temp, species1, species2) %>% unique() #grab unique interactions
  nullsetup <- nullmodel(table(temp), method = "quasiswap") #shuffle setup
  out <- simulate(nullsetup, nsim=1) #grab one iteration
  rg <- igraph::graph_from_incidence_matrix(out[,,1]) #make it into a graph (easier to extract in nice format)
  
  Vtemp <- igraph::as_data_frame(rg, "vertices") %>% unique()
  Vset <- rbind(Vset, Vtemp) #add to our total set of vertices
  Etemp <- igraph::as_data_frame(rg)
  Eset <- rbind(Eset, Etemp) #add to our total set of edges
  }
  Vset <- unique(Vset) #Grab our unique verts
  Eset <- unique(Eset) #same for edges

  metatemp <- graph_from_data_frame(Eset, directed = FALSE, vertices = Vset$name) #Create our newly shuffled metaweb
  
  #Calculate centrality metrics on the new null web
  bmetaCent_temp <- data.frame(between=igraph::centralization.betweenness(metatemp)$res, 
             close=igraph::centralization.closeness(metatemp)$res,
             deg=igraph::centralization.degree(metatemp, mode="all")$res,
             eig=igraph::centralization.evcent(metatemp)$vector,
             node=V(metatemp)$name,
             indexID=i)
 bmetaCent_null <- rbind(bmetaCent_null, bmetaCent_temp) #rbind to our set of interactions
 print(paste(i, " complete", sep=" "))
}

dist_bmetaCent_null <- bmetaCent_null %>% dplyr::group_by(., node) %>% dplyr::summarise(., meanclose=mean(close, na.rm=T), sdclose=sd(close, na.rm=T)) #Now that we have a bunch of iteractions, find the distribution

#### Now we repeat for insects
Vset <- NULL
Eset <- NULL
imetaCent_null <- NULL
nsim <- 3
for(i in 1:nsim){ #Iterate over each local network
  for(j in 1:length(unique(Insectweb$site_index))){ #Reshuffle on each local network
  temp <- Insectweb[Insectweb$site_index==j,] #grab the local
  
    if(nrow(temp)<3){ #If there's less than 3 nodes skip it
    print("too few")
    next
  }
  temp <- dplyr::select(temp, species1, species2) %>% unique() #grab unique interactions
  nullsetup <- nullmodel(table(temp), method = "quasiswap") #shuffle setup
  if(nullsetup$ncol==1){ #If we don't have at least one record to swap, just skip
    next
  }
    if(nullsetup$nrow==1){
    next
  }
  out <- simulate(nullsetup, nsim=1) #grab one iteration
  rg <- igraph::graph_from_incidence_matrix(out[,,1]) #make it into a graph (easier to extract in nice format)
  
  Vtemp <- igraph::as_data_frame(rg, "vertices") %>% unique()
  Vset <- rbind(Vset, Vtemp) #add to our total set of vertices
  Etemp <- igraph::as_data_frame(rg)
  Eset <- rbind(Eset, Etemp) #add to our total set of edges
  }
  Vset <- unique(Vset) #Grab our unique verts
  Eset <- unique(Eset) #same for edges

  metatemp <- graph_from_data_frame(Eset, directed = FALSE, vertices = Vset$name) #Create our newly shuffled metaweb
  
  #Calculate centrality metrics on the new null web
  imetaCent_temp <- data.frame(between=igraph::centralization.betweenness(metatemp)$res, 
             close=igraph::centralization.closeness(metatemp)$res,
             deg=igraph::centralization.degree(metatemp, mode="all")$res,
             eig=igraph::centralization.evcent(metatemp)$vector,
             node=V(metatemp)$name,
             indexID=i)
 imetaCent_null <- rbind(imetaCent_null, imetaCent_temp) #rbind to our set of interactions
}

dist_imetaCent_null <- imetaCent_null %>% dplyr::group_by(., node) %>% dplyr::summarise(., meanclose=mean(close, na.rm=T), sdclose=sd(close, na.rm=T)) #Now that we have a bunch of iterations, find the distribution
#save(dist_imetaCent_null, file="dist_imetaCent_null.Rda")
```

Loading in the results we found on the local machine
```{r}
load(file="data/Parallelwebs.RDA")
```


Now let's calculate our z-score of realized global closeness compared to the null. Nearly of these are significantly less central than expected from the null randomization. 

```{r}
bmetaCent <- left_join(bmetaCent, dist_bmetaCent_null, by="node")
imetaCent <- left_join(imetaCent, dist_imetaCent_null, by="node")

bmetaCent$close.z <- (bmetaCent$close-bmetaCent$meanclose)/bmetaCent$sdclose
imetaCent$close.z <- (imetaCent$close-imetaCent$meanclose)/imetaCent$sdclose
```
Investigating why we get crazy z-scores
```{r}
net <- dplyr::filter(Insectweb, network_name=="M_PL_062")
table(net$species1)

plot(x=composite_z$sdclose, y=abs(composite_z$close.z))

```



```{r}
composite_z <- rbind(dplyr::select(imetaCent, envarea, globkm, node, type, net, close.z), dplyr::select(bmetaCent, envarea, globkm, node, type, net, close.z)) %>% dplyr::filter(., is.na(envarea)==F)
composite_z <- dplyr::filter(imetaCent, is.na(envarea)==F)

composite_z$type[composite_z$type %in% c("Insect", "Bird")] <- "Floral Visitor"

plot(x=composite_z$close.z, y=composite_z$sdclose)


geop1_z <- composite_z %>% 
  ggplot(., aes(x=scale(log(globkm)), y=close.z, col=net))+
  geom_point(alpha=0.5)+
  geom_smooth(method="lm")+
  facet_wrap(~type, labeller = labeller(type = c("Floral Visitors", "Plants")))+
  theme_classic()+
  xlab("Scaled Log Geographic Area")+
  ylab("Closeness Centrality  (z-transformed)")+guides(col=guide_legend(title="MetaNetwork"))+
  scale_color_manual(labels = c("Avian-Plant", "Insect-Plant"), values = c("#0F882C", "dodgerblue"))+
  theme(legend.position=c(0.53,.21), guide_legend(override.aes=list(fill=NA)))

envp1_z <- composite_z %>% 
  ggplot(., aes(x=scale(log(envarea)), y=close.z, col=net))+
  geom_point(alpha=0.5)+
  geom_smooth(method="lm")+
  facet_wrap(~type)+
  theme_classic()+
  xlab("Scaled Log Environmental Area")+
  ylab("Closeness Centrality (z-transformed)")+guides(col="none")+
  scale_color_manual(labels = c("Avian-Plant", "Insect-Plant"), values = c("#0F882C", "dodgerblue"))

#pdf(file="figs/metaweb_centrality_ztrans.pdf", width=6, height=6)
grid.arrange(geop1_z, envp1_z, nrow=2)
#dev.off()
```

```{r}
inmod_globr <- glm(close
~scale(log(envarea))+as.factor(type)+scale(log(globkm)), data=imetaCent)
summary(inmod_globr)

inmod_globz <- glm(close.z
~scale(log(envarea))+as.factor(type)+scale(log(globkm)), data=imetaCent)
summary(inmod_globz)

bnmod_globr <- glm(close
~scale(log(envarea))+as.factor(type)+scale(log(globkm)), data=bmetaCent)
summary(bnmod_globr)

bnmod_globz <- glm(close.z
~scale(log(envarea))+as.factor(type)+scale(log(globkm)), data=imetaCent)
summary(bnmod_globz)
```
Looking at interaction turnover with respect to Geographic Range size. What is "interaction turnover" at the speceis level? Maybe just beta diversity of partners

```{r}
library(labdsv)
library(BAT)
Lan <- Birdweb[Birdweb$species1=="Lantana camara",]
Lan <- Lan %>% dplyr::select(network_name,species2) %>% 
  dplyr::mutate(., presence=1) %>%
  matrify()

beta <- BAT::beta.multi(Lan, func="soerensen", abund=F)[1]
bmetaCent

# Create a named list of matrices for each unique species1
mat_list <- dplyr::select(bmetaCent, node, nsites) %>%
  dplyr::rename(., species1=node) %>%
  left_join(Birdweb, .) %>% 
  dplyr::filter(., nsites>1) %>%
  dplyr::select(species1, network_name, species2) %>%
  dplyr::mutate(presence = 1) %>%
  nest(data = c(network_name, species2, presence)) %>%
  mutate(mat = map(data, ~ matrify(data.frame(.x)))) %>%
  select(species1, mat)

# Apply BAT::beta.multi to each matrix
beta_sp1 <- mat_list %>%
  mutate(beta = map(mat, ~ BAT::beta.multi(.x, func = "soerensen", abund = FALSE)[1]))

# Repeat for unique species2
mat_list <- dplyr::select(bmetaCent, node, nsites) %>%
  dplyr::rename(., species2=node) %>%
  left_join(Birdweb, .) %>% 
  dplyr::filter(., nsites>1) %>%
  dplyr::select(species1, network_name, species2) %>%
  dplyr::mutate(presence = 1) %>%
  nest(data = c(network_name, species1, presence)) %>%
  mutate(mat = map(data, ~ matrify(data.frame(.x)))) %>%
  select(species2, mat)

# Apply BAT::beta.multi to each matrix
beta_sp2 <- mat_list %>%
  mutate(beta = map(mat, ~ BAT::beta.multi(.x, func = "soerensen", abund = FALSE)[1]))

# Optionally extract the scalar beta value into a separate column
beta_summary <- beta_sp1 %>%
  mutate(beta_value = map_dbl(beta, 1)) %>%
  select(species1, beta_value)

length(unique(imetaCent$node))
```




## Supplement

```{r}
bmetaCent %>% ggplot(., aes(x=localmeanclose, y=close, col=log(nsites)))+
  xlab("Mean Local Closeness")+
  ylab("Global Closeness")+theme_classic()+
  geom_point()

imetaCent %>% ggplot(., aes(x=localmeanclose, y=close, col=log(nsites)))+
  xlab("Mean Local Closeness")+
  ylab("Global Closeness")+theme_classic()+
  geom_point()


bmetaCent %>% ggplot(., aes(x=localmeanclose.z, y=close.z, col=log(nsites)))+
  xlab("Mean Local Closeness (z-transformed)")+
  ylab("Global Closeness (z-transformed)")+theme_classic()+ 
  geom_errorbar(aes(xmin = localmeanclose.z-1.96*sdclose, xmax = localmeanclose.z+1.96*sdclose), width = 0)+
  geom_point()

imetaCent %>% ggplot(., aes(x=localmeanclose, y=close, col=log(nsites)))+
  xlab("Mean Local Closeness")+
  ylab("Global Closeness")+theme_classic()+ 
  geom_errorbar(aes(xmin = localmeanclose-1.96*sdclose, xmax = localmeanclose+1.96*sdclose), width = 0)+
  geom_point()
```


Comparing variable importance: A random forest approach
```{r}
localirf <- imetaCent %>% dplyr::select(envarea, globkm, type, nsites, localmeanclose.z) %>% na.omit() %>% randomForest::randomForest(localmeanclose.z
 ~., data=., ntree=10000, importance = T)

metairf <- imetaCent %>% dplyr::select(envarea, globkm, type, nsites, close) %>% na.omit() %>% randomForest::randomForest(close
 ~., data=., ntree=10000, importance = T)

localbrf <- bmetaCent %>% dplyr::select(envarea, globkm, type, nsites, localmeanclose.z) %>% na.omit() %>% randomForest::randomForest(localmeanclose.z
 ~., data=., ntree=10000, importance = T)

metabrf <- bmetaCent %>% dplyr::select(envarea, globkm, type, nsites, close) %>% na.omit() %>% randomForest::randomForest(close
 ~., data=., ntree=10000, importance = T)

imp <- data.frame(vars=c("envarea","globkm","type","nsites"), 
locinsectimp=localirf$importance[,"%IncMSE"], locinsectvar=localirf$importanceSD,
metainsectimp=metairf$importance[,"%IncMSE"], metainsectvar=metairf$importanceSD,
locbirdimp=localbrf$importance[,"%IncMSE"], locbirdvar=localbrf$importanceSD,
metabirdimp=metabrf$importance[,"%IncMSE"], metabirdvar=localbrf$importanceSD
)

imp_long <- data.frame(vars=rep(c("envarea","globkm","type","nsites"),4), 
           model=c(rep("insect_local", 4), rep("insect_meta", 4), rep("bird_local", 4), rep("bird_meta", 4)),
            importance=c(localirf$importance[,"%IncMSE"], metairf$importance[,"%IncMSE"], localbrf$importance[,"%IncMSE"], metabrf$importance[,"%IncMSE"]),
           sd=c(localirf$importanceSD, metairf$importanceSD, localbrf$importanceSD, metabrf$importanceSD))
           
imp_long <- imp_long %>% group_by(., model) %>% 
  dplyr::mutate(., relImportance=importance/max(importance), relSD=sd/max(importance)) %>%
  ungroup()


pdf(file="figs/RF_importance.pdf", width=8, height=8)
ggplot(data=imp_long, aes(y=vars, x=relImportance, fill=model))+
  geom_col(position = position_dodge(), width = 0.9)+
  theme_classic()+
  geom_errorbar(aes(xmin=relImportance-relSD, xmax=relImportance+relSD), width=.1,
                 position=position_dodge(.9))+
  scale_fill_manual(values = c("bird_local" = alpha("#0F882C", 0.5),
                                "bird_meta" = "#0F882C",
                                "insect_local" = alpha("dodgerblue", 0.5),
                                "insect_meta" = "dodgerblue"),
                    labels = c(
      "bird_local" = "Local Centrality (Avian)",
      "bird_meta" = "Metaweb Centrality (Avian)",
      "insect_local" = "Local Centrality (Insect)",
      "insect_meta" = "Metaweb Centrality (Insect)"
    ))+
  xlab("Relative Importance")+
  ylab("Variable")+
  scale_y_discrete(labels = c(
    "envarea" = "Environmental Range",
    "globkm" = "Geographic Range",
    "type" = "Node Class",
    "nsites" = "Number of Sites"
  ))
dev.off()

```


Aside: Are Centrality metrics actually correlated with each other?

```{r}
imetaCent[,1:4]
metaCent <- imetaCent
pear_mat <- cor(imetaCent[,1:4], method="pearson", use="complete.obs")
spearmat <- cor(metaCent[,1:4], method="spearman", use="complete.obs")


parpl <- list()
for(j in 1:4){
parpl[[j]] <- ggplot(metaCent, aes(x=metaCent[,1], y=metaCent[,j]))+geom_point()+xlab("between")+ylab(colnames(metaCent)[j])
}
for(j in 1:4){
parpl[[j+4]] <- ggplot(metaCent, aes(x=metaCent[,2], y=metaCent[,j]))+geom_point()+xlab("close")+ylab(colnames(metaCent)[j])
}
for(j in 1:4){
parpl[[j+8]] <- ggplot(metaCent, aes(x=metaCent[,3], y=metaCent[,j]))+geom_point()+xlab("deg")+ylab(colnames(metaCent)[j])
}
for(j in 1:4){
parpl[[j+12]] <- ggplot(metaCent, aes(x=metaCent[,4], y=metaCent[,j]))+geom_point()+xlab("eig")+ylab(colnames(metaCent)[j])
}

#pdf(file="figs/PairwiseCors.pdf", width=11, height=11)
grid.arrange(parpl[[1]], 
             parpl[[2]], 
             parpl[[3]],
             parpl[[4]],
             parpl[[5]],
             parpl[[6]],
             parpl[[7]],
             parpl[[8]],
             parpl[[9]],
             parpl[[10]],
             parpl[[11]],
             parpl[[12]],
             parpl[[13]],
             parpl[[14]],
             parpl[[15]],
             parpl[[16]],
             nrow = 4)
#dev.off()


#pdf(file="figs/CentralityCorrelations.pdf", width=8, height=4)
par(mfrow = c(1, 2))
colnames(pear_mat) <- c("Betweenness", "Closeness", "Degree", "Eigenvector")
rownames(pear_mat) <- c("Betweenness", "Closeness", "Degree", "Eigenvector")
corrplot::corrplot(pear_mat, method="color",type = "upper", diag=F, main="Pearson's Correlation", mar=c(0,0,2,0), cl.cex = 0.5, addCoef.col="black")

colnames(spearmat) <- c("Betweenness", "Closeness", "Degree", "Eigenvector")
rownames(spearmat) <- c("Betweenness", "Closeness", "Degree", "Eigenvector")
corrplot::corrplot(spearmat, type = "upper", diag=F, main="Spearman's Correlation", mar=c(0,0,2,0), method="color", cl.cex = 0.5, addCoef.col="black")
#dev.off()
```


Aside: Here's a version with a much more liberal null for standardization: shuffling the entire network, without preserving individual number of links per node. Very rough and not pursued. 
```{r}
nits <- 1000

rndout <- NULL
for(j in 1:nits){
  #Generate a random graph based on the constraints of our empirical local network
  rg <- igraph::sample_bipartite(n1=length(V(tbig)[V(tbig)$type==F]),#n of first node class
                     n2=length(V(tbig)[V(tbig)$type==T]),#n of second node class
                     m=length(E(tbig)),#Number of edges
                     type="gnm") #Specify we're generating with fixed # of links
  
  V(rg)$component <- components(rg)$membership #Assign component membership
  rg <- delete.vertices(rg, V(rg)$component!=which.max(components(rg)$csize)) #Remove vertices that aren't included in the largest component        
  
  rgCent <- data.frame(between=igraph::centralization.betweenness(rg)$res,
               close=igraph::centralization.closeness(rg)$res,
               deg=igraph::centralization.degree(rg, mode="all")$res,
               eig=igraph::centralization.evcent(rg)$vector,
               site_index=i)
  rndout <- rbind(rgCent, rndout)
}

hist(rndout$close)

length(rndout$close[tmetaCent$close[4]<rndout$close])/length(rndout$close)

dplyr::mutate(tmetaCent, z.close=length(rndout$close[close<rndout$close])/length(rndout$close))
dplyr::mutate(tmetaCent, z.close=length(close))
```


 Huh. Standardized metaweb centrality is alomst always 0, or close to it. Potentially due to inherent spatial structure of the component networks? (I.E. there's underlying spatial to the structure, and when you start randomizing connections without reguard to that then the null draws are almost always more well connected)
```{r}
#First, need to randomize the bird metanetworks for comparability
  rndout <- NULL
  nullBirdMeta <- nullmodel(table(BirdMeta), method = "quasiswap")
  out <- simulate(nullBirdMeta, nsim=1000) #Set up our null model object (see vegan vignette)
  for(simID in 1:1000){
    rg <- igraph::graph_from_incidence_matrix(out[,,simID])
    V(rg)$component <- components(rg)$membership #Assign component membership
    rg <- delete.vertices(rg, V(rg)$component!=which.max(components(rg)$csize)) #Remove vertices that aren't included in the largest component    
    rgCent <- data.frame(between=igraph::centralization.betweenness(rg)$res,
                 close=igraph::centralization.closeness(rg)$res,
                 deg=igraph::centralization.degree(rg, mode="all")$res,
                 eig=igraph::centralization.evcent(rg)$vector,
                 site_index=i, #Grab the site
                 sim=simID,
                 node=V(rg)$name) #Which simulation is this
    rndout <- rbind(rgCent, rndout)
  }
  
  bmetaCent$z.close.meta <- NA
  for(j in unique(bmetaCent$node)){ #Perform ranking for each node
    ret <- dplyr::filter(rndout, node==j) #Find all of the simulated values for a given node
    emp <- dplyr::filter(bmetaCent, node==j) #Grab the empirical value
    bmetaCent$z.close.meta[bmetaCent$node==j] <- sum(emp$close[1]>ret$close)/length(ret$close) #assign a z-score based on empirical value
}

hist(bmetaCent$z.close.meta, breaks=25, xlab="Z-transformed closeness", main="Z-transformed closeness of nodes in bird metaweb")


#First, Repeat the above for comparability
  rndout <- NULL
  nullBirdMeta <- nullmodel(table(InsectMeta), method = "quasiswap")
  out <- simulate(nullBirdMeta, nsim=1000) #Set up our null model object (see vegan vignette)
  for(simID in 1:1000){
    rg <- igraph::graph_from_incidence_matrix(out[,,simID])
    V(rg)$component <- components(rg)$membership #Assign component membership
    rg <- delete.vertices(rg, V(rg)$component!=which.max(components(rg)$csize)) #Remove vertices that aren't included in the largest component    
    rgCent <- data.frame(between=igraph::centralization.betweenness(rg)$res,
                 close=igraph::centralization.closeness(rg)$res,
                 deg=igraph::centralization.degree(rg, mode="all")$res,
                 eig=igraph::centralization.evcent(rg)$vector,
                 site_index=i, #Grab the site
                 sim=simID,
                 node=V(rg)$name) #Which simulation is this
    rndout <- rbind(rgCent, rndout)
  }
  
  bmetaCent$z.close.meta <- NA
  for(j in unique(bmetaCent$node)){ #Perform ranking for each node
    ret <- dplyr::filter(rndout, node==j) #Find all of the simulated values for a given node
    emp <- dplyr::filter(bmetaCent, node==j) #Grab the empirical value
    bmetaCent$z.close.meta[bmetaCent$node==j] <- sum(emp$close[1]>ret$close)/length(ret$close) #assign a z-score based on empirical value
  }
  
plot(x=scale(bmetaCent$close), y=scale(bmetaCent$z.close.meta))
```
