---
title: "TITLE"
author: "AUTHORS"
includes:
  in_header:
    - \usepackage{lmodern}
output:
  pdf_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    toc: yes
  html_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    theme: journal
---


```{r}
library(igraph)
#library(dplyr)
#library(ggplot2)
library(gridExtra)
library(rgbif)
library(curl)
#library(tidyr)
library(jsonlite)
library(tidyverse)
library(taxize)
library(vegan)
```

Let's start with querying WOL for plant-pollinator datasets. 


Querying the web of life API. 
Tutorial for how to do this found here: https://www.web-of-life.es/tutorial/session-download-data.html
```{r}
# define the base url
base_url <- "https://www.web-of-life.es/"   
json_url2 <- paste0(base_url,"get_networks.php?interaction_type=Pollination") 

WolPols <- jsonlite::fromJSON(json_url2)
WolMeta <- read.csv(paste0(base_url,"get_network_info.php")) %>%dplyr::filter(., network_type%in%"Pollination")
length(unique(WolPols$network_name)) # 174 Networks

WolMeta <- read.csv(paste0(base_url,"get_network_info.php"))
WolMeta <- WolMeta %>% dplyr::filter(., network_type%in%"Pollination") #Make sure we have only pollination
WolMeta <- WolMeta %>% 
  #dplyr::select(., network_name, region, latitude, longitude) %>% 
  left_join(WolPols, ., by="network_name")
```

Let's do some double checking to 
1) Separate vertebrate from invertebrate pollination networks
%2) Make different sources are correctly harmonized #Turns out these are the new deal

I was first going check every taxa with taxize, but turns out this actually takes a long time to run with so many taxa. Instead, I looked at the original papers for the 74 publications included in these data. Slow, but still faster than taxize. I load in the key I created for that below. 

```{r}
studykey <- read.csv(file="studykey.csv")
WolMeta <- left_join(WolMeta, studykey, by=c("author", "reference"))

WolMeta<- dplyr::filter(WolMeta, grepl("Unidentified", species2, ignore.case=F)==F) #remove unidentified
WolMeta<- dplyr::filter(WolMeta, grepl(" sp[1-9]+", species2, ignore.case=F)==F) #remove those with polls identified to genera only
WolMeta<- dplyr::filter(WolMeta, grepl(" sp[1-9]+", species1, ignore.case=F)==F) #remove those plants identified to genera only
#Interesting to evaluate whether to do this on a local level, but necessary with global metaweb (sp1 in one network may be sp2 in another, etc)

mixedwebs <- dplyr::filter(WolMeta, Taxa=="Mixed")
Insectweb <- dplyr::filter(WolMeta, Taxa=="Insecta")
Birdweb <- dplyr::filter(WolMeta, Taxa=="Aves")

Insectweb <- dplyr::filter(mixedwebs, grepl(c("Apis"), species2)==T | grepl(c("Ornidia"), species2)==T | grepl(c("Bombus"), species2)==T | grepl(c("Musca"), species2)==T ) %>% rbind(Insectweb, .) #Add in some common insect genera from mixed webs

mixedwebs <- dplyr::filter(mixedwebs, grepl(c("Apis"), species2)==F & grepl(c("Ornidia"), species2)==F & grepl(c("Bombus"), species2)==F & grepl(c("Musca"), species2)==F ) #Remove these from the to-query group


mixedord <- tax_name(unique(mixedwebs$species2), get = "class", db = "ncbi")

missing <- dplyr::filter(mixedord, is.na(class)==T)
missing$query[missing$query=="Politmus milleri"] <- "Polytmus milleri" #Mispelled bird
missing$query[missing$query=="Physiphoa azurea"] <- "Physiphora azurea " #Mispelled fly

missing$gen <- gsub( " .*$", "", missing$query) 
gens <- data.frame(gen=missing$gen, class=NA) %>% unique()
gens <- dplyr::filter(gens, gen %in% c("Clamirius", "Eurymetopun")==F) #Can't find these

gens$class[gens$gen%in%c("Amazilia", "Carduelis", "Foudia", "Polytmus")] <- "Aves" #The birds in the list
gens$class[is.na(gens$class)==T] <- "Insect" #Everything left is an insect 

missing <- missing %>% dplyr::select(., -class) %>% left_join(., gens, by="gen") %>% na.omit() #Grab the missing classes

Birdweb  <- dplyr::filter(mixedwebs, species2 %in% missing$query[missing$class=="Aves"]) %>%
  rbind(Birdweb,.)
Insectweb <- dplyr::filter(mixedwebs, species2 %in% missing$query[missing$class=="Insecta"]) %>%
  rbind(Insectweb,.)

```

Now that we've done our filtering, let's check out our two created metawebs
```{r, eval=F}
InsectMeta <- dplyr::select(Insectweb, species1, species2) %>% unique()
imeta <- igraph::graph_from_data_frame(InsectMeta, directed=F) #Create idgraph object


BirdMeta <- dplyr::select(Birdweb, species1, species2) %>% unique()
bmeta <- igraph::graph_from_data_frame(BirdMeta, directed=F) #Create idgraph object
save(InsectMeta, imeta, BirdMeta, bmeta, file="data/metawebs.RDA")
```

Load in the data from above so we don't have to repeat our query
```{r}
load("data/metawebs.RDA")
```


Need to remove species not located in the main component of the metaweb (otherwise can't compute centrality)
```{r}
V(imeta)$component <- components(imeta)$membership
components(imeta)$csize #Largest component has 6237 nodes; the rest are isolated pairs
imeta <- delete.vertices(imeta, V(imeta)$component!=which.max(components(imeta)$csize)) #Remove vertices that aren't included in the largest component
table(V(imeta)$component)



V(bmeta)$component <- components(bmeta)$membership
components(bmeta)$csize #Largest component has 721 nodes; the rest are isolated pairs
bmeta <- delete.vertices(bmeta, V(bmeta)$component!=which.max(components(bmeta)$csize)) #Remove vertices that aren't included in the largest component
table(V(bmeta)$component)
```


Let's calculate our measures of species centrality in the metaweb

```{r}
imetaCent <- data.frame(between=igraph::centralization.betweenness(imeta)$res,
           close=igraph::centralization.closeness(imeta)$res,
           deg=igraph::centralization.degree(imeta, mode="all")$res,
           eig=igraph::centralization.evcent(imeta)$vector,
           node=V(imeta)$name)

bmetaCent <- data.frame(between=igraph::centralization.betweenness(bmeta)$res,
           close=igraph::centralization.closeness(bmeta)$res,
           deg=igraph::centralization.degree(bmeta, mode="all")$res,
           eig=igraph::centralization.evcent(bmeta)$vector,
           node=V(bmeta)$name)

## Use n equally spaced breaks to assign each value to n-1 equal sized bins 
ii <- cut(bmetaCent$eig, breaks = seq(min(bmetaCent$eig, na.rm=T), max(bmetaCent$eig, na.rm=T), len = 100), 
          include.lowest = TRUE)

## Use bin indices, ii, to select color from vector of n-1 equally spaced colors
V(bmeta)$color <- colorRampPalette(c("lightblue", "blue"))(99)[ii]


plot(bmeta, vertex.label=NA, layout=layout_nicely)
```



For the few plant species present in both insect and bird networks, is their centrality similiar in both networks? In short: No
```{r}
overlaps <- dplyr::filter(bmetaCent, node %in% imetaCent$node)

overlaps <- imetaCent %>% dplyr::select(node, deg, eig, close) %>% dplyr::rename(., insect_deg=deg, insect_eig=eig, insect_close=close) %>% left_join(overlaps, ., by="node")

plot(overlaps$eig, overlaps$insect_eig, xlab="Eigenvalue Centrality in Bird Network", ylab="Eigenvalue Centrality in Insect Network")
cor.test(overlaps$eig, overlaps$insect_eig)
plot(overlaps$deg, overlaps$insect_deg, xlab="Degree in Bird Network", ylab="Degree in Insect Network")
cor.test(overlaps$deg, overlaps$insect_deg)

plot(overlaps$close, overlaps$insect_close, xlab="Closeness in Bird Network", ylab="Closeness in Insect Network")
cor.test(overlaps$close, overlaps$insect_close)
```


```{r}
sp <- unique(imetaCent$node, bmetaCent$node)
length(sp)
```

Let's actually look at geographic ranges
```{r}
georng <- read.csv(file="data/geosummaryout.csv") 
envrng <- read.csv(file="data/envsummaryout.csv")
```

Add envriornmental range to our existing data
```{r}
envrng$node <- envrng$file
envrng$node <- gsub("_", " ", envrng$node)
envrng$node <- gsub(".csv", "", envrng$node)
envrng$node <- paste(toupper(substring(envrng$node, 1, 1)), substring(envrng$node, 2), sep="")

imetaCent <- dplyr::select(envrng, envarea, node) %>% left_join(imetaCent, ., by="node")
bmetaCent <- dplyr::select(envrng, envarea, node) %>% left_join(bmetaCent, ., by="node")
```

Add geographic range size to the data quality
```{r}
colnames(georng)
globgeo <- georng %>% 
  dplyr::group_by(., file) %>% 
  dplyr::summarise(., globkm=sum(contgeokm.area))

globgeo$node <- globgeo$file
globgeo$node <- gsub("_", " ", globgeo$node)
globgeo$node <- gsub(".csv", "", globgeo$node)
globgeo$node <- paste(toupper(substring(globgeo$node, 1, 1)), substring(globgeo$node, 2), sep="") 
globgeo <- dplyr::select(globgeo, -file)

imetaCent <- left_join(imetaCent, globgeo, by="node")
bmetaCent <- left_join(bmetaCent, globgeo, by="node")
```


Add a columns so we can separate our taxa if we desire
```{r}
imetaCent$type <- NA
imetaCent$type[imetaCent$node %in% InsectMeta$species1] <- "Plant"
imetaCent$type[imetaCent$node %in% InsectMeta$species2] <- "Insect"

bmetaCent$type <- NA
bmetaCent$type[bmetaCent$node %in% BirdMeta$species1] <- "Plant"
bmetaCent$type[bmetaCent$node %in% BirdMeta$species2] <- "Bird"

hist(imetaCent$eig)
hist(imetaCent$close)
```

Investigative plotting of relationship between envrionmental range and centrality

```{r}
imetaCent %>% #dplyr::filter(., close<0.5) %>% 
  ggplot(., aes(x=scale(log(envarea)), y=close, col=type))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~type)+
  theme_classic()+
  xlab("Scaled Log Enviornmental Area")+
  ylab("Closeness Centrality")


bmetaCent %>% dplyr::filter(., close<0.5) %>% 
  ggplot(., aes(x=scale(log(envarea)), y=close, col=type))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~type)+
  theme_classic()+
  xlab("Scaled Log Enviornmental Area")+
  ylab("Closeness Centrality")

hist(scale(log(imetaCent$envarea)))
```


```{r}
imetaCentmodat <- imetaCent
imetaCentmodat <- dplyr::filter(imetaCentmodat, close<0.5)

inmod <- lm(close~scale(log(envarea))+as.factor(type)+as.factor(type)*scale(log(envarea))+scale(log(globkm))+as.factor(type)*scale(log(globkm)), data=imetaCentmodat)
plot(inmod)
summary(inmod)

bmetaCentmodat <- bmetaCent
bmetaCentmodat <- dplyr::filter(bmetaCentmodat, close<0.5)
bmod <- lm(close~scale(log(envarea))+as.factor(type)+as.factor(type)*scale(log(envarea))+scale(log(globkm))+as.factor(type)*scale(log(globkm)), data=bmetaCentmodat)
summary(bmod)
plot(bmod)

```

```{r}
imetaCent %>% dplyr::filter(., close<0.5) %>% 
  ggplot(., aes(x=scale(log(globkm)), y=close, col=type))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~type)+
  theme_classic()+
  xlab("Scaled Geographic Area")+
  ylab("Closeness Centrality")


bmetaCent %>% dplyr::filter(., close<0.5) %>% 
  ggplot(., aes(x=scale(log(globkm)), y=close, col=type))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~type)+
  theme_classic()+
  xlab("Scaled Geographic Area")+
  ylab("Closeness Centrality")
```
Let's make some slightly prettier plots for this

```{r}
imetaCent$net <- "Insect"
bmetaCent$net <- "Bird"
composite <- rbind(dplyr::select(imetaCent, envarea, globkm, node, type, net, close), dplyr::select(bmetaCent, envarea, globkm, node, type, net, close)) %>% dplyr::filter(., is.na(envarea)==F)

unique(composite$type)

composite$type[composite$type %in% c("Insect", "Bird")] <- "Floral Visitor"

geop1 <- composite %>% dplyr::filter(., close<0.5) %>% 
  ggplot(., aes(x=scale(log(globkm)), y=close, col=net))+
  geom_point(alpha=0.5)+
  geom_smooth(method="lm")+
  facet_wrap(~type, labeller = labeller(type = c("Floral Visitors", "Plants")))+
  theme_classic()+
  xlab("Scaled Log Geographic Area")+
  ylab("Closeness Centrality")+guides(col=guide_legend(title="MetaNetwork"))+
  scale_color_manual(labels = c("Avian-Plant", "Insect-Plant"), values = c("#0F882C", "dodgerblue"))+
  theme(legend.position=c(0.11,.81), guide_legend(override.aes=list(fill=NA)))

envp1 <- composite %>% dplyr::filter(., close<0.5) %>% 
  ggplot(., aes(x=scale(log(envarea)), y=close, col=net))+
  geom_point(alpha=0.5)+
  geom_smooth(method="lm")+
  facet_wrap(~type)+
  theme_classic()+
  xlab("Scaled Log Environmental Area")+
  ylab("Closeness Centrality")+guides(col="none")+
  scale_color_manual(labels = c("Avian-Plant", "Insect-Plant"), values = c("#0F882C", "dodgerblue"))
```

Fig at the metaweb level
```{r}
#pdf(file="figs/metaweb_area_scaling.pdf", width=6, height=6)
grid.arrange(geop1, envp1, nrow=2)
#dev.off()
```



Some of the networks with different IDs actually are sampled at the same site (potentially from different years, etc). I'd like to combine each of these into site-specific rather than study specific, so I add a siteindex here below. 
```{r}
Birdweb <- Birdweb %>%
  group_by(latitude, longitude) %>%
  mutate(site_index = cur_group_id()) %>%
  ungroup()

length(unique(Birdweb$network_name))
length(unique(Birdweb$site_index))


Insectweb <- Insectweb %>%
  group_by(latitude, longitude) %>%
  mutate(site_index = cur_group_id()) %>%
  ungroup()

length(unique(Insectweb$network_name))
length(unique(Insectweb$site_index))
```
 
 Let's calculate centrality on a local level for each node of the networks that make up our metawebs. 
 
 This takes a while, so I'm setting default=F and loading outputs below. 
```{r, eval=F}

localiCent <- NULL
for(i in 1:length(unique(Insectweb$site_index))){
    temp <- Insectweb[Insectweb$site_index==i,]
      if(nrow(temp)<4){ #if too small a network, skip it
      next
    }
    
    temp <- dplyr::select(temp, species1, species2) %>% unique() #grab unique interactions
    tmeta <- igraph::graph_from_data_frame(temp, directed=F) #Create igraph object
    tbig <- igraph::graph_from_incidence_matrix(table(temp)) #Create a large network where we don't do component drop (for null model later)
    
    V(tmeta)$component <- components(tmeta)$membership #Assign component membership
    tmeta <- igraph::delete.vertices(tmeta, V(tmeta)$component!=which.max(components(tmeta)$csize)) #Remove vertices that aren't included in the largest component
    
    tmetaCent <- data.frame(between=igraph::centralization.betweenness(tmeta)$res, #Calculate our centrality measures (locally)
               close=igraph::centralization.closeness(tmeta)$res,
               deg=igraph::centralization.degree(tmeta, mode="all")$res,
               eig=igraph::centralization.evcent(tmeta)$vector,
               node=V(tmeta)$name,
               site_index=i)
    #Now we have our actual metric, but we need a null model approach
    ## Perform z-score standardization
    rndout <- NULL
    nullsetup <- nullmodel(table(temp), method = "quasiswap")
    out <- simulate(nullsetup, nsim=1000) #Set up our null model object (see vegan vignette)
    for(simID in 1:1000){
      rg <- igraph::graph_from_incidence_matrix(out[,,simID])
      V(rg)$component <- components(rg)$membership #Assign component membership
      rg <- delete.vertices(rg, V(rg)$component!=which.max(components(rg)$csize)) #Remove vertices that aren't included in the largest component    
      rgCent <- data.frame(between=igraph::centralization.betweenness(rg)$res,
                   close=igraph::centralization.closeness(rg)$res,
                   deg=igraph::centralization.degree(rg, mode="all")$res,
                   eig=igraph::centralization.evcent(rg)$vector,
                   site_index=i, #Grab the site
                   sim=simID,
                   node=V(rg)$name) #Which simulation is this
      rndout <- rbind(rgCent, rndout)
    }
    #Calculate the z-score
    tmetaCent$z.close <- NA
    for(j in 1:nrow(tmetaCent)){ #Perform ranking for each node
      ret <- dplyr::filter(rndout, node==tmetaCent$node[j]) #Find all of the simulated values for a given node
      emp <- dplyr::filter(tmetaCent, node==tmetaCent$node[j]) #Grab the empirical value
      tmetaCent$z.close[tmetaCent$node==ret$node[j]] <-sum(emp$close>ret$close)/length(ret$close) #assign a z-score based on empirical value
    localiCent <- rbind(localiCent, tmetaCent)
  }
}




localbCent <- NULL
for(i in 1:length(unique(Birdweb$site_index))){ #Iterate over each local network
  temp <- Birdweb[Birdweb$site_index==i,]
    if(nrow(temp)<4){ #if too small a network, skip it
    next
  }
  
  temp <- dplyr::select(temp, species1, species2) %>% unique() #grab unique interactions
  tmeta <- igraph::graph_from_data_frame(temp, directed=F) #Create igraph object
  
  V(tmeta)$component <- components(tmeta)$membership #Assign component membership
  tmeta <- delete.vertices(tmeta, V(tmeta)$component!=which.max(components(tmeta)$csize)) #Remove vertices that aren't included in the largest component
  
  #Calculate centrality metrics (raw)
  tmetaCent <- data.frame(between=igraph::centralization.betweenness(tmeta)$res, 
             close=igraph::centralization.closeness(tmeta)$res,
             deg=igraph::centralization.degree(tmeta, mode="all")$res,
             eig=igraph::centralization.evcent(tmeta)$vector,
             node=V(tmeta)$name,
             site_index=i)
  
  ## Perform z-score standardization
  rndout <- NULL
  nullsetup <- nullmodel(table(temp), method = "quasiswap")
  out <- simulate(nullsetup, nsim=1000) #Set up our null model object (see vegan vignette)
  for(simID in 1:1000){
    rg <- igraph::graph_from_incidence_matrix(out[,,simID])
    V(rg)$component <- components(rg)$membership #Assign component membership
    rg <- delete.vertices(rg, V(rg)$component!=which.max(components(rg)$csize)) #Remove vertices that aren't included in the largest component    
    rgCent <- data.frame(between=igraph::centralization.betweenness(rg)$res,
                 close=igraph::centralization.closeness(rg)$res,
                 deg=igraph::centralization.degree(rg, mode="all")$res,
                 eig=igraph::centralization.evcent(rg)$vector,
                 site_index=i, #Grab the site
                 sim=simID,
                 node=V(rg)$name) #Which simulation is this
    rndout <- rbind(rgCent, rndout)
  }
  #Calculate the z-score
  tmetaCent$z.close <- NA
  for(j in 1:nrow(tmetaCent)){ #Perform ranking for each node
    ret <- dplyr::filter(rndout, node==tmetaCent$node[j]) #Find all of the simulated values for a given node
    emp <- dplyr::filter(tmetaCent, node==tmetaCent$node[j]) #Grab the empirical value
    tmetaCent$z.close[tmetaCent$node==ret$node[j]] <-sum(emp$close>ret$close)/length(ret$close) #assign a z-score based on empirical value
  }
  #Save our local metric to the larger dataset
  localbCent <- rbind(localbCent, tmetaCent)
}

#save(localbCent, localiCent, file="data/z_localCent.RDA")
```


```{r}
load(file="data/z_localCent.RDA")


localiz <-localiCent %>% #Take the summary output
  group_by(., node) %>% #grab for each node
  dplyr::summarise(., nsites=length(unique(site_index)), localmeanclose=mean(close), localmeanclose.z=mean(z.close, na.rm=T)) %>% #Find mean of each nodes average local centralities, both z-tranformed and not
  ungroup()

imetaCent <- dplyr::left_join(imetaCent, localiz, by="node") #Add local  measure back to metaWeb version

imetaCent %>% ggplot(., aes(x=localmeanclose,y=close, col=log(nsites)))+
  geom_point()+
  xlab("Mean Local Closeness")+
  ylab("Global Closeness")+theme_classic()

imetaCent %>% ggplot(., aes(x=localmeanclose.z,y=localmeanclose, col=log(nsites)))+
  geom_point()+
  xlab("Mean Local Closeness (Z-transformed)")+
  ylab("Mean Local Closeness (Non-transformed)")+theme_classic()


localbz <-localbCent %>% #Take the summary output
  group_by(., node) %>% #grab for each node
  dplyr::summarise(., nsites=length(unique(site_index)), localmeanclose=mean(close), localmeanclose.z=mean(z.close, na.rm=T)) %>% #Find mean of each nodes average local centralities, both z-tranformed and not
  ungroup()

bmetaCent <- dplyr::left_join(bmetaCent, localbz, by="node") #Add local  measure back to metaWeb version

bmetaCent %>% ggplot(., aes(x=localmeanclose,y=close, col=log(nsites)))+
  geom_point()+
  xlab("Mean Local Closeness")+
  ylab("Global Closeness")+theme_classic()

bmetaCent %>% ggplot(., aes(x=localmeanclose.z,y=localmeanclose, col=log(nsites)))+
  geom_point()+
  xlab("Mean Local Closeness (Z-transformed)")+
  ylab("Mean Local Closeness (Non-transformed)")+theme_classic()

```
 



## Supplement

Aside: Are Centrality metrics actually correlated with each other?

```{r}
imetaCent[,1:4]
metaCent <- imetaCent
pear_mat <- cor(imetaCent[,1:4], method="pearson", use="complete.obs")
spearmat <- cor(metaCent[,1:4], method="spearman", use="complete.obs")


parpl <- list()
for(j in 1:4){
parpl[[j]] <- ggplot(metaCent, aes(x=metaCent[,1], y=metaCent[,j]))+geom_point()+xlab("between")+ylab(colnames(metaCent)[j])
}
for(j in 1:4){
parpl[[j+4]] <- ggplot(metaCent, aes(x=metaCent[,2], y=metaCent[,j]))+geom_point()+xlab("close")+ylab(colnames(metaCent)[j])
}
for(j in 1:4){
parpl[[j+8]] <- ggplot(metaCent, aes(x=metaCent[,3], y=metaCent[,j]))+geom_point()+xlab("deg")+ylab(colnames(metaCent)[j])
}
for(j in 1:4){
parpl[[j+12]] <- ggplot(metaCent, aes(x=metaCent[,4], y=metaCent[,j]))+geom_point()+xlab("eig")+ylab(colnames(metaCent)[j])
}

#pdf(file="figs/PairwiseCors.pdf", width=11, height=11)
grid.arrange(parpl[[1]], 
             parpl[[2]], 
             parpl[[3]],
             parpl[[4]],
             parpl[[5]],
             parpl[[6]],
             parpl[[7]],
             parpl[[8]],
             parpl[[9]],
             parpl[[10]],
             parpl[[11]],
             parpl[[12]],
             parpl[[13]],
             parpl[[14]],
             parpl[[15]],
             parpl[[16]],
             nrow = 4)
#dev.off()


#pdf(file="figs/CentralityCorrelations.pdf", width=8, height=4)
par(mfrow = c(1, 2))
colnames(pear_mat) <- c("Betweenness", "Closeness", "Degree", "Eigenvector")
rownames(pear_mat) <- c("Betweenness", "Closeness", "Degree", "Eigenvector")
corrplot::corrplot(pear_mat, method="color",type = "upper", diag=F, main="Pearson's Correlation", mar=c(0,0,2,0), cl.cex = 0.5, addCoef.col="black")

colnames(spearmat) <- c("Betweenness", "Closeness", "Degree", "Eigenvector")
rownames(spearmat) <- c("Betweenness", "Closeness", "Degree", "Eigenvector")
corrplot::corrplot(spearmat, type = "upper", diag=F, main="Spearman's Correlation", mar=c(0,0,2,0), method="color", cl.cex = 0.5, addCoef.col="black")
#dev.off()
```


Aside: Here's a version with a much more liberal null for standardization: shuffling the entire network, without preserving individual number of links per node. Very rough and not pursued. 
```{r}
nits <- 1000

rndout <- NULL
for(j in 1:nits){
  #Generate a random graph based on the constraints of our empirical local network
  rg <- igraph::sample_bipartite(n1=length(V(tbig)[V(tbig)$type==F]),#n of first node class
                     n2=length(V(tbig)[V(tbig)$type==T]),#n of second node class
                     m=length(E(tbig)),#Number of edges
                     type="gnm") #Specify we're generating with fixed # of links
  
  V(rg)$component <- components(rg)$membership #Assign component membership
  rg <- delete.vertices(rg, V(rg)$component!=which.max(components(rg)$csize)) #Remove vertices that aren't included in the largest component        
  
  rgCent <- data.frame(between=igraph::centralization.betweenness(rg)$res,
               close=igraph::centralization.closeness(rg)$res,
               deg=igraph::centralization.degree(rg, mode="all")$res,
               eig=igraph::centralization.evcent(rg)$vector,
               site_index=i)
  rndout <- rbind(rgCent, rndout)
}

hist(rndout$close)

length(rndout$close[tmetaCent$close[4]<rndout$close])/length(rndout$close)

dplyr::mutate(tmetaCent, z.close=length(rndout$close[close<rndout$close])/length(rndout$close))
dplyr::mutate(tmetaCent, z.close=length(close))
```
 
