---
title: "Clean Analysis"
author: "Grant Foster"
date: "2025-06-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Libraries
```{r}
library(igraph)
#library(dplyr)
#library(ggplot2)
library(gridExtra)
library(rgbif)
library(curl)
#library(tidyr)
library(jsonlite)
library(tidyverse)
library(taxize)
library(vegan)
library(randomForest)
library(gridExtra)
library(vegan)
library(ggridges)
library(brms)

set.seed(1)
```


## Data Prep
Let's start with querying WOL for plant-pollinator datasets. 

Querying the web of life API. 
Tutorial for how to do this found here: https://www.web-of-life.es/tutorial/session-download-data.html
```{r, eval=F}
# define the base url
base_url <- "https://www.web-of-life.es/"   
json_url2 <- paste0(base_url,"get_networks.php?interaction_type=Pollination") 

WolPols <- jsonlite::fromJSON(json_url2)
WolMeta <- read.csv(paste0(base_url,"get_network_info.php")) %>%dplyr::filter(., network_type%in%"Pollination")
length(unique(WolPols$network_name)) # 174 Networks

WolMeta <- read.csv(paste0(base_url,"get_network_info.php"))
WolMeta <- WolMeta %>% dplyr::filter(., network_type%in%"Pollination") #Make sure we have only pollination
WolMeta <- WolMeta %>% 
  #dplyr::select(., network_name, region, latitude, longitude) %>% 
  left_join(WolPols, ., by="network_name")
#WolMeta <- dplyr::select(WolMeta, -Taxa.y) %>% dplyr::rename(., Taxa=Taxa.x)
```

Let's do some double checking to 
1) Separate vertebrate from invertebrate pollination networks
%2) Make different sources are correctly harmonized #Turns out these are the new deal

I was first going check every taxa with taxize, but turns out this actually takes a long time to run with so many taxa. Instead, I looked at the original papers for the 74 publications included in these data. Slow, but still faster than taxize. I load in the key I created for that below. 

```{r, eval=FALSE}
studykey <- read.csv(file="studykey.csv")
WolMeta <- left_join(WolMeta, studykey, by=c("author", "reference"))

WolMeta<- dplyr::filter(WolMeta, grepl("Unidentified", species2, ignore.case=F)==F) #remove unidentified
WolMeta<- dplyr::filter(WolMeta, grepl(" sp[1-9]+", species2, ignore.case=F)==F) #remove those with polls identified to genera only
WolMeta<- dplyr::filter(WolMeta, grepl(" sp[1-9]+", species1, ignore.case=F)==F) #remove those plants identified to genera only
#Interesting to evaluate whether to do this on a local level, but necessary with global metaweb (sp1 in one network may be sp2 in another, etc)

mixedwebs <- dplyr::filter(WolMeta, Taxa=="Mixed")
Insectweb <- dplyr::filter(WolMeta, Taxa=="Insecta")
Birdweb <- dplyr::filter(WolMeta, Taxa=="Aves")

Insectweb <- dplyr::filter(mixedwebs, grepl(c("Apis"), species2)==T | grepl(c("Ornidia"), species2)==T | grepl(c("Bombus"), species2)==T | grepl(c("Musca"), species2)==T ) %>% rbind(Insectweb, .) #Add in some common insect genera from mixed webs

mixedwebs <- dplyr::filter(mixedwebs, grepl(c("Apis"), species2)==F & grepl(c("Ornidia"), species2)==F & grepl(c("Bombus"), species2)==F & grepl(c("Musca"), species2)==F ) #Remove these from the to-query group


mixedord <- tax_name(unique(mixedwebs$species2), get = "class", db = "ncbi")

missing <- dplyr::filter(mixedord, is.na(class)==T)
missing$query[missing$query=="Politmus milleri"] <- "Polytmus milleri" #Mispelled bird
missing$query[missing$query=="Physiphoa azurea"] <- "Physiphora azurea " #Mispelled fly

missing$gen <- gsub( " .*$", "", missing$query) 
gens <- data.frame(gen=missing$gen, class=NA) %>% unique()
gens <- dplyr::filter(gens, gen %in% c("Clamirius", "Eurymetopun")==F) #Can't find these

gens$class[gens$gen%in%c("Amazilia", "Carduelis", "Foudia", "Polytmus")] <- "Aves" #The birds in the list
gens$class[is.na(gens$class)==T] <- "Insect" #Everything left is an insect 

missing <- missing %>% dplyr::select(., -class) %>% left_join(., gens, by="gen") %>% na.omit() #Grab the missing classes

Birdweb  <- dplyr::filter(mixedwebs, species2 %in% missing$query[missing$class=="Aves"]) %>%
  rbind(Birdweb,.)
Insectweb <- dplyr::filter(mixedwebs, species2 %in% missing$query[missing$class=="Insecta"]) %>%
  rbind(Insectweb,.)

#Now that we've done our filtering, let's check out our two created metawebs
InsectMeta <- dplyr::select(Insectweb, species1, species2) %>% unique()
imeta <- igraph::graph_from_data_frame(InsectMeta, directed=F) #Create igraph object


BirdMeta <- dplyr::select(Birdweb, species1, species2) %>% unique()
bmeta <- igraph::graph_from_data_frame(BirdMeta, directed=F) #Create igraph object



#Creating the site index
Birdweb <- Birdweb %>%
  group_by(latitude, longitude) %>%
  mutate(site_index = cur_group_id()) %>%
  ungroup()

Insectweb <- Insectweb %>%
  group_by(latitude, longitude) %>%
  mutate(site_index = cur_group_id()) %>%
  ungroup()

save(InsectMeta, imeta, BirdMeta, bmeta, file="cleanData/metawebs.RDA")
save(Birdweb, Insectweb, file="cleanData/localwebs.RDA") #Save the individual webs
```

A quick check-in point, loading in our metaweb data (both in igraph and df forms)
```{r}
load("cleanData/metawebs.RDA")
```

Computing Baseline Centrality Metrics on the Metawebs

First need to drop disconnected components
```{r, eval=FALSE}
V(imeta)$component <- components(imeta)$membership
#components(imeta)$csize #Largest component has 6237 nodes; the rest are isolated pairs
imeta <- delete.vertices(imeta, V(imeta)$component!=which.max(components(imeta)$csize)) #Remove vertices that aren't included in the largest component
#table(V(imeta)$component)

V(bmeta)$component <- components(bmeta)$membership
#components(bmeta)$csize #Largest component has 719 nodes; the rest are isolated pairs
bmeta <- delete.vertices(bmeta, V(bmeta)$component!=which.max(components(bmeta)$csize)) #Remove vertices that aren't included in the largest component
#table(V(bmeta)$component)
```

Now that we have singular components we can calculate centrality for each of these networks. imetaCent/bmetaCent are our main units of analysis for our metaweb metrics. 
```{r, eval=FALSE}
imetaCent <- data.frame(between=igraph::centralization.betweenness(imeta)$res,
           close=igraph::centralization.closeness(imeta)$res,
           deg=igraph::centralization.degree(imeta, mode="all")$res,
           eig=igraph::centralization.evcent(imeta)$vector,
           node=V(imeta)$name)

bmetaCent <- data.frame(between=igraph::centralization.betweenness(bmeta)$res,
           close=igraph::centralization.closeness(bmeta)$res,
           deg=igraph::centralization.degree(bmeta, mode="all")$res,
           eig=igraph::centralization.evcent(bmeta)$vector,
           node=V(bmeta)$name)
```


Contending with Range size: 

```{r, eval=FALSE}
georng <- read.csv(file="data/geosummaryout.csv") 
envrng <- read.csv(file="data/envsummaryout.csv")

envrng$node <- envrng$file #file contains the queried node name
envrng$node <- gsub("_", " ", envrng$node) #this and below some string manipulations for joins
envrng$node <- gsub(".csv", "", envrng$node)
envrng$node <- paste(toupper(substring(envrng$node, 1, 1)), substring(envrng$node, 2), sep="")

imetaCent <- dplyr::select(envrng, envarea, node) %>% left_join(imetaCent, ., by="node") #Add in environmental ranges
bmetaCent <- dplyr::select(envrng, envarea, node) %>% left_join(bmetaCent, ., by="node")
 

globgeo <- georng %>% 
  dplyr::group_by(., file) %>% 
  dplyr::summarise(., globkm=sum(contgeokm.area)) #Combine individual continent ranges into single range size value

globgeo$node <- globgeo$file
globgeo$node <- gsub("_", " ", globgeo$node)
globgeo$node <- gsub(".csv", "", globgeo$node)
globgeo$node <- paste(toupper(substring(globgeo$node, 1, 1)), substring(globgeo$node, 2), sep="") 
globgeo <- dplyr::select(globgeo, -file)

imetaCent <- left_join(imetaCent, globgeo, by="node") #add geo ranges
bmetaCent <- left_join(bmetaCent, globgeo, by="node")

rm(envrng, georng, globgeo) #Now that we've joined, removing for clutter
```

Adding a type argument for ease of use
```{r, eval=FALSE}
imetaCent$type <- NA
imetaCent$type[imetaCent$node %in% Insectweb$species1] <- "Plant"
imetaCent$type[imetaCent$node %in% Insectweb$species2] <- "Insect"

bmetaCent$type <- NA
bmetaCent$type[bmetaCent$node %in% Birdweb$species1] <- "Plant"
bmetaCent$type[bmetaCent$node %in% Birdweb$species2] <- "Bird"
```

Now, let's work on getting a z-standardization for species centrality in the metaweb. The following code shuffles individual local webs (maintaining rown and columnsums), recombines them into a new simulated metaweb, and calculates species centrality in that created web. This is done for an arbitrary number of times (2k), creating a distribution we can use for z-standardization. This is parallalelized for speed, and outputs are provided.
```{r, eval=FALSE}
library(parallel)
library(igraph)
library(dplyr)

#Most of the parallel version of this code was written by ChatGPT using the following prompt:Hey ChatGPT, use the parallel package in R to parallelize this code across an arbitrary number of cores. 

load(file="cleanData/localwebs.RDA")

# Define number of cores and simulations
ncores <- detectCores() - 2 #leave an extra core to appease the daemons
cl <- makeCluster(ncores)

clusterEvalQ(cl, { #Make sure workers have necessary libraries
  library(igraph)
  library(dplyr)
  library(vegan)
})

# Export necessary data and functions to the cluster
clusterExport(cl, varlist = c("Birdweb", "Insectweb"))

# Function to process Birdweb simulations
bird_sim_fun <- function(i) {
  Vset <- NULL
  Eset <- NULL
  #lay <- layout_as_bipartite(rg)
  for (j in unique(Birdweb$site_index)) {
    temp <- Birdweb[Birdweb$site_index == j, ]
    if (nrow(temp) < 3) next
    temp <- dplyr::select(temp, species1, species2) %>% unique()
    nullsetup <- vegan::nullmodel(table(temp), method = "quasiswap")
    out <- simulate(nullsetup, nsim = 1)
    if(j!=20) {rg <- igraph::graph_from_incidence_matrix(out[, , 1])}
    if(j==20) {rg <- igraph::graph_from_incidence_matrix(table(temp$species1, temp$species2))}
    
    #plot(rg, layout=lay)
    Vtemp <- igraph::as_data_frame(rg, "vertices") %>% unique()
    Vset <- rbind(Vset, Vtemp) #Vertex list across all sites
    Etemp <- igraph::as_data_frame(rg)
    Eset <- rbind(Eset, Etemp) #Edge list across all sites
    print(j)
  }
  if (is.null(Eset) || is.null(Vset)) return(NULL)
  Vset <- unique(Vset)
  Eset <- unique(Eset)
  metatemp <- graph_from_data_frame(Eset, directed = FALSE, vertices = Vset$name)
  
  bmetaCent_temp <- data.frame(
    between = igraph::centralization.betweenness(metatemp)$res,
    close   = igraph::centralization.closeness(metatemp)$res,
    deg     = igraph::centralization.degree(metatemp, mode = "all")$res,
    eig     = igraph::centralization.evcent(metatemp)$vector,
    node    = V(metatemp)$name,
    indexID = i
  )
  return(bmetaCent_temp)
}

# # Function to process Insectweb simulations
insect_sim_fun <- function(i) {
  Vset <- NULL
  Eset <- NULL

  for (j in unique(Insectweb$site_index)) {
    print(paste("starting", j))
    temp <- Insectweb[Insectweb$site_index == j, ]
    if (nrow(temp) < 3) next
    temp <- dplyr::select(temp, species1, species2) %>% unique()
    nullsetup <- vegan::nullmodel(table(temp), method = "greedyqswap")
    if (nullsetup$ncol == 1 || nullsetup$nrow == 1) next
    out <- simulate(nullsetup, nsim = 1, thin=1)
    if(j!="space") {rg <- igraph::graph_from_incidence_matrix(out[, , 1])}
    #if(j==47) {rg <- igraph::graph_from_incidence_matrix(table(temp$species1, temp$species2))}
    #rg <- igraph::graph_from_incidence_matrix(out[, , 1])
    Vtemp <- igraph::as_data_frame(rg, "vertices") %>% unique()
    Vset <- rbind(Vset, Vtemp)
    Etemp <- igraph::as_data_frame(rg)
    Eset <- rbind(Eset, Etemp)
  }
  if (is.null(Eset) || is.null(Vset)) return(NULL)
  Vset <- unique(Vset)
  Eset <- unique(Eset)
  metatemp <- graph_from_data_frame(Eset, directed = FALSE, vertices = Vset$name)

  imetaCent_temp <- data.frame(
    between = igraph::centralization.betweenness(metatemp)$res,
    close   = igraph::centralization.closeness(metatemp)$res,
    deg     = igraph::centralization.degree(metatemp, mode = "all")$res,
    eig     = igraph::centralization.evcent(metatemp)$vector,
    node    = V(metatemp)$name,
    indexID = i
  )
  return(imetaCent_temp)
}

# Run simulations in parallel
nsim <- 2000
bmetaCent_list <- parLapply(cl, 1:nsim, bird_sim_fun)
imetaCent_list <- parLapply(cl, 1:nsim, insect_sim_fun)


# Combine and post-process
bmetaCent_null <- do.call(rbind, bmetaCent_list)
imetaCent_null <- do.call(rbind, imetaCent_list)

# Save results
save(bmetaCent_null, file = "cleanData/BmetawebSwaps_raw2k_newrun.Rda") #Save the output
save(imetaCent_null, file = "cleanData/ImetawebSwaps_raw2k_newrun.Rda")

# Stop the cluster
stopCluster(cl)

```


Now adding in the output of z-standardization

```{r, eval=FALSE}
load(file="cleanData/BmetawebSwaps_raw2k.Rda")
load(file="cleanData/ImetawebSwaps_raw2k.Rda")

bsums <- dplyr::group_by(bmetaCent_null, node) %>%
  dplyr::summarise(., meancl=mean(close), sdcl=sd(close)) #summarise the individual

bmetaCent <- left_join(bmetaCent,bsums, by="node")
bmetaCent$close.z <- (bmetaCent$close-bmetaCent$meancl)/bmetaCent$sdcl

isums <- dplyr::group_by(imetaCent_null, node) %>%
  dplyr::summarise(., meancl=mean(close), sdcl=sd(close)) #summarise the individual

imetaCent <- left_join(imetaCent,isums, by="node")
imetaCent$close.z <- (imetaCent$close-imetaCent$meancl)/imetaCent$sdcl

rm(imetaCent_null, isums, bmetaCent_null, bsums) #remove intermediate objects to reduce clutter

save(imetaCent, imeta, bmetaCent, bmeta, file="cleanData/metaCent.Rda") #Saving the output
```

Load in our objects from above.
```{r}
load("cleanData/metaCent.Rda")
load(file="cleanData/localwebs.RDA")
```

Our metaweb should be ready for analysis. Now let's work on our local webs.
```{r, eval=FALSE}
# Get unique site indices
site_indices <- unique(Insectweb$site_index)

# Setup cluster
n_cores <- detectCores() - 1
cl <- makeCluster(n_cores)

# Export necessary variables and functions to workers
clusterExport(cl, varlist = c("Insectweb"), envir = environment())
clusterEvalQ(cl, {
  library(igraph)
  library(vegan)
  library(dplyr)
})

# Parallelized version of your per-site loop
localiCent_list <- parLapply(cl, site_indices, function(i) {
  temp <- Insectweb[Insectweb$site_index == i, ]
  if (nrow(temp) < 4) return(NULL)

  temp <- dplyr::select(temp, species1, species2) %>% unique()
  tmeta <- igraph::graph_from_data_frame(temp, directed = FALSE)
  tbig <- igraph::graph_from_incidence_matrix(table(temp))

  V(tmeta)$component <- components(tmeta)$membership
  tmeta <- igraph::delete.vertices(tmeta, V(tmeta)$component != which.max(components(tmeta)$csize))

  tmetaCent <- data.frame(
    between = igraph::centralization.betweenness(tmeta)$res,
    close   = igraph::centralization.closeness(tmeta)$res,
    deg     = igraph::centralization.degree(tmeta, mode = "all")$res,
    eig     = igraph::centralization.evcent(tmeta)$vector,
    node    = V(tmeta)$name,
    site_index = i
  )

  # Null model simulation
  nullsetup <- nullmodel(table(temp), method = "quasiswap")
  sims <- simulate(nullsetup, nsim = 1000)
  rndout <- list()

  for (simID in 1:1000) {
    rg <- igraph::graph_from_incidence_matrix(sims[,,simID])
    V(rg)$component <- components(rg)$membership
    rg <- delete.vertices(rg, V(rg)$component != which.max(components(rg)$csize))

    rgCent <- data.frame(
      between = igraph::centralization.betweenness(rg)$res,
      close   = igraph::centralization.closeness(rg)$res,
      deg     = igraph::centralization.degree(rg, mode = "all")$res,
      eig     = igraph::centralization.evcent(rg)$vector,
      site_index = i,
      sim = simID,
      node = V(rg)$name
    )

    rndout[[simID]] <- rgCent
  }

  rndout_df <- do.call(rbind, rndout)

  # Z-score for closeness
  tmetaCent$z.close <- sapply(tmetaCent$node, function(n) {
    sim_vals <- dplyr::filter(rndout_df, node == n)
    emp_val  <- dplyr::filter(tmetaCent, node == n)
    if (nrow(sim_vals) > 1 && sd(sim_vals$close, na.rm = TRUE) > 0) {
      (emp_val$close - mean(sim_vals$close, na.rm = TRUE)) / sd(sim_vals$close, na.rm = TRUE)
    } else {
      NA
    }
  })

  return(tmetaCent)
})

# Stop the cluster
stopCluster(cl)

# Combine all results
localiCent <- do.call(rbind, localiCent_list)



 ########NOW BIRDS
# Get unique site indices
site_indices <- unique(Birdweb$site_index)

# Setup cluster
n_cores <- detectCores() - 1
cl <- makeCluster(n_cores)

# Export necessary variables and functions to workers
clusterExport(cl, varlist = c("Birdweb"), envir = environment())
clusterEvalQ(cl, {
  library(igraph)
  library(vegan)
  library(dplyr)
})

# Parallelized version of your per-site loop
localbCent_list <- parLapply(cl, site_indices, function(i) {
  temp <- Birdweb[Birdweb$site_index == i, ]
  if (nrow(temp) < 4) return(NULL)

  temp <- dplyr::select(temp, species1, species2) %>% unique()
  tmeta <- igraph::graph_from_data_frame(temp, directed = FALSE)
  tbig <- igraph::graph_from_incidence_matrix(table(temp))

  V(tmeta)$component <- components(tmeta)$membership
  tmeta <- igraph::delete.vertices(tmeta, V(tmeta)$component != which.max(components(tmeta)$csize))

  tmetaCent <- data.frame(
    between = igraph::centralization.betweenness(tmeta)$res,
    close   = igraph::centralization.closeness(tmeta)$res,
    deg     = igraph::centralization.degree(tmeta, mode = "all")$res,
    eig     = igraph::centralization.evcent(tmeta)$vector,
    node    = V(tmeta)$name,
    site_index = i
  )

  # Null model simulation
  nullsetup <- nullmodel(table(temp), method = "quasiswap")
  sims <- simulate(nullsetup, nsim = 1000) #Grab 1k simulations
  rndout <- list()

  for (simID in 1:1000) { #Go through each local simulation and find the z-score
    rg <- igraph::graph_from_incidence_matrix(sims[,,simID])
    V(rg)$component <- components(rg)$membership
    rg <- delete.vertices(rg, V(rg)$component != which.max(components(rg)$csize))

    rgCent <- data.frame(
      between = igraph::centralization.betweenness(rg)$res,
      close   = igraph::centralization.closeness(rg)$res,
      deg     = igraph::centralization.degree(rg, mode = "all")$res,
      eig     = igraph::centralization.evcent(rg)$vector,
      site_index = i,
      sim = simID,
      node = V(rg)$name
    )

    rndout[[simID]] <- rgCent
  }

  rndout_df <- do.call(rbind, rndout)

  # Z-score for closeness
  tmetaCent$z.close <- sapply(tmetaCent$node, function(n) {
    sim_vals <- dplyr::filter(rndout_df, node == n)
    emp_val  <- dplyr::filter(tmetaCent, node == n)
    if (nrow(sim_vals) > 1 && sd(sim_vals$close, na.rm = TRUE) > 0) {
      (emp_val$close - mean(sim_vals$close, na.rm = TRUE)) / sd(sim_vals$close, na.rm = TRUE)
    } else {
      NA
    }
  })

  return(tmetaCent)
})

# Stop the cluster
stopCluster(cl)
rm(cl)

# Combine all results
localbCent <- do.call(rbind, localbCent_list)

```

Now that we've got the z-transformed versions of our local centrality, we can add back in our range data. 
```{r, eval=FALSE}
localbCent <- bmetaCent %>% 
  dplyr::select(., node, envarea, globkm) %>% #add in ranges
  left_join(localbCent, by="node")

localiCent <- imetaCent %>% 
  dplyr::select(., node, envarea, globkm) %>% #add in ranges
  left_join(localiCent, by="node")
save(localiCent, localbCent, file="cleanData/localCentrality.Rda")
```

Now we can load in data back for our local networks
```{r}
rm(InsectMeta, BirdMeta) #remove objects used for making these
load(file="cleanData/localCentrality.Rda")
```


## Analysis
```{r}
imetaCent$net <- "Insect"
bmetaCent$net <- "Bird"

compositeMeta <- rbind(imetaCent, bmetaCent) %>% dplyr::filter(., is.na(envarea)==F)
compositeMeta$type[compositeMeta$type %in% c("Insect", "Bird")] <- "Floral Visitor"
```


Linear models for the effect of range size on centrality of each of our network X nodetype combinations
```{r, eval=FALSE}
#Raw values
insectVisitor <- imetaCent %>% dplyr::filter(., type=="Insect") %>%
  lm(data=., formula=close~scale(log(globkm))+scale(log(envarea))+scale(log(globkm))*scale(log(envarea)))
summary(insectVisitor)



library(brms)

bayes.brms <- imetaCent %>% 
  dplyr::filter(., type=="Insect") %>%
  brm(close~scale(log(globkm))+scale(log(envarea))+scale(log(globkm))*scale(log(envarea)), 
                  family = gaussian(), #gaussian error
                  data = .,
                  prior=set_prior("normal(0, 2)", class = "b"), #heirarchical prior-all slopes will use this
                  chains = 5, # nb of chains
                  iter = 5000, # nb of iterations, including burnin
                  warmup = 1000, # burnin
                  thin = 1) # no thinning


#plot(bayes.brms)
#pp_check(bayes.brms, ndraws = 100, type = 'ecdf_overlay')
#prior_summary(bayes.brms)
#pairs(bayes.brms)

samps <- as_draws_df(bayes.brms)

#stanplot(bayes.brms, type = "areas", prob = 0.95)
#stancode(bayes.brms)
```


```{r}
#Sig in geo raw: Visiting Insects, Insect-Visited Plants, Bird-Visited Plants
clrs <- c("#845ec2", "#00896f")
  
geoRngMeta <- compositeMeta %>% 
  ggplot(., aes(x=scale(log(globkm)), y=close, col=net))+
  geom_point(alpha=0.7)+
  geom_smooth(method="lm", data=dplyr::filter(compositeMeta, type!="Floral Visitor" | net=="Insect"))+ #Remove insignificant coefficients from the lm data
  facet_wrap(~type, labeller = labeller(type = c("Floral Visitors", "Plants")))+
  theme_classic()+
  xlab("Scaled Log Geographic Area")+
  ylab("Closeness Centrality in \n Global Metaweb ")+guides(col=guide_legend(title="MetaNetwork"))+
  scale_color_manual(labels = c("Avian-Plant", "Insect-Plant"), values = clrs)+
  theme(legend.position=c(0.15,.85), guide_legend(override.aes=list(fill=NA)))+
       theme(strip.text.x = element_text(size = 14))

#Sig in env raw: Insect-Visited Plants
envRngMeta <- compositeMeta %>% 
  ggplot(., aes(x=scale(log(envarea)), y=close, col=net))+
  geom_point(alpha=0.7)+
  geom_smooth(method="lm", data=dplyr::filter(compositeMeta, type=="Plant" & net=="Insect"))+
  facet_wrap(~type)+
  theme_classic()+
  xlab("Scaled Log Environmental Area")+
  ylab("Closeness Centrality in \n Global Metaweb ")+guides(col="none")+
  scale_color_manual(labels = c("Avian-Plant", "Insect-Plant"), values = clrs)+
       theme(strip.text.x = element_text(size = 14))

#Sig in geo.z: Bird-Visited Plants
geoRngMeta.z <- compositeMeta %>% 
  ggplot(., aes(x=scale(log(globkm)), y=close.z, col=net))+
  geom_point(alpha=0.7)+
  geom_smooth(method="lm", data=dplyr::filter(compositeMeta, type=="Plant" & net=="Bird"))+
  facet_wrap(~type)+
  theme_classic()+
  xlab("Scaled Log Geographic Area")+
  ylab("Closeness Centrality in \n Global Metaweb (Z-transformed)")+guides(col="none")+
  scale_color_manual(labels = c("Avian-Plant", "Insect-Plant"), values = clrs)+
       theme(strip.text.x = element_text(size = 14))

#Sig in env.z: Insect-Visited Plants, Bird-Visited Plants
envRngMeta.z <- compositeMeta %>% 
  ggplot(., aes(x=scale(log(envarea)), y=close.z, col=net))+
  geom_point(alpha=0.7)+
  geom_smooth(method="lm", data=dplyr::filter(compositeMeta, type=="Plant"))+
  facet_wrap(~type)+
  theme_classic()+
  xlab("Scaled Log Environmental Area")+
  ylab("Closeness Centrality in \n Global Metaweb (Z-transformed)")+guides(col="none")+
  scale_color_manual(labels = c("Avian-Plant", "Insect-Plant"), values = clrs)+
       theme(strip.text.x = element_text(size = 14))

#pdf(file="cleanFigs/MetawebCentralityPlot.pdf", width=10, height=8)
grid.arrange(geoRngMeta, geoRngMeta.z, envRngMeta, envRngMeta.z, nrow=2)
#dev.off()
```

Now looking at the local networks. Let's create a compositeLocal object we can use as our unit of analysis. 
```{r}
localiCent$net <- "Insect"
localbCent$net <- "Bird"

localiCent$type <- NA
localiCent$type[localiCent$node %in% Insectweb$species1] <- "Plant"
localiCent$type[localiCent$node %in% Insectweb$species2] <- "Insect"

localbCent$type <- NA
localbCent$type[localbCent$node %in% Birdweb$species1] <- "Plant"
localbCent$type[localbCent$node %in% Birdweb$species2] <- "Bird"

compositeLocal <- rbind(localbCent, localiCent) %>% dplyr::filter(., is.na(net)==F)
compositeLocal$type[compositeLocal$type %in% c("Insect", "Bird")] <- "Floral Visitor" 
```

# Performing linear models
```{r, eval=FALSE}
#Raw values
insectVisitorLocal <- localiCent %>% dplyr::filter(., type=="Insect") %>%
  lm(data=., formula=close~scale(log(globkm))+scale(log(envarea))+scale(log(globkm))*scale(log(envarea)))
summary(insectVisitorLocal)

insectPlantLocal <- localiCent %>% dplyr::filter(., type=="Plant") %>%
  lm(data=., formula=close~scale(log(globkm))+scale(log(envarea))+scale(log(globkm))*scale(log(envarea)))
summary(insectPlantLocal)

birdVisitorLocal <- localbCent %>% dplyr::filter(., type=="Bird") %>%
  lm(data=., formula=close~scale(log(globkm))+scale(log(envarea))+scale(log(globkm))*scale(log(envarea)))
summary(birdVisitorLocal)

birdPlantLocal <- localbCent %>% dplyr::filter(., type=="Plant") %>%
  lm(data=., formula=close~scale(log(globkm))+scale(log(envarea))+scale(log(globkm))*scale(log(envarea)))
summary(birdPlantLocal)

#Z-transformations
insectVisitor.zLocal <- localiCent %>% dplyr::filter(., type=="Insect") %>%
  lm(data=., formula=z.close~scale(log(globkm))+scale(log(envarea))+scale(log(globkm))*scale(log(envarea)))
summary(insectVisitor.zLocal)

insectPlant.zLocal <- localiCent %>% dplyr::filter(., type=="Plant") %>%
  lm(data=., formula=z.close~scale(log(globkm))+scale(log(envarea))+scale(log(globkm))*scale(log(envarea)))
summary(insectPlant.zLocal)

birdVisitor.zLocal <- localbCent %>% dplyr::filter(., type=="Bird") %>%
  lm(data=., formula=z.close~scale(log(globkm))+scale(log(envarea))+scale(log(globkm))*scale(log(envarea)))
summary(birdVisitor.zLocal)

birdPlant.zLocal <- localbCent %>% dplyr::filter(., type=="Plant") %>%
  lm(data=., formula=z.close~scale(log(globkm))+scale(log(envarea))+scale(log(globkm))*scale(log(envarea)))
summary(birdPlant.zLocal)

car::vif(insectVisitorLocal, type="predictor")
car::vif(insectVisitorLocal, type="predictor")
car::vif(insectPlantLocal, type="predictor")
car::vif(birdVisitorLocal, type="predictor")
car::vif(birdPlantLocal, type="predictor")

car::vif(insectVisitor.zLocal, type="predictor")
car::vif(insectPlant.zLocal, type="predictor")
car::vif(birdVisitor.zLocal, type="predictor")
car::vif(birdPlant.zLocal, type="predictor")
```

Alternative: Do we get generally the same results using a Bayesian framework? 
```{r}

bayesRunclose <- function(netype, nodetype){
  if(netype=="Insect"){
    bayesamp <- imetaCent %>% dplyr::filter(., type==nodetype) %>% #Grab network
    dplyr::filter(., is.na(globkm)==F & is.na(envarea)==F) %>% #filter to complete cases
  MCMCglmm::MCMCglmm(fixed=close~scale(log(globkm))+scale(log(envarea))+scale(log(globkm))*scale(log(envarea)), data=., thin=1, burnin=10000,nitt=20000)
  }
  
  if(netype=="Bird"){
    bayesamp <- bmetaCent %>% dplyr::filter(., type==nodetype) %>% #Grab network
    dplyr::filter(., is.na(globkm)==F & is.na(envarea)==F) %>% #filter to complete cases
  MCMCglmm::MCMCglmm(fixed=close~scale(log(globkm))+scale(log(envarea))+scale(log(globkm))*scale(log(envarea)), data=., thin=1)
  }
  
  bayesdf <- data.frame(bayesamp$Sol) #extract samples
  colnames(bayesdf) <- c("Intercept", "geo", "env", "interaction")
  bayesdf$type <- nodetype
  bayesdf$net <- netype
  bayeslong <- pivot_longer(bayesdf, cols=c(1:4), names_to="param")
  return(bayeslong)
}
```


```{r}
Insect_visitor.brms <- imetaCent %>% 
  dplyr::filter(., type=="Insect") %>%
  brm(close~scale(log(globkm))+scale(log(envarea))+scale(log(globkm))*scale(log(envarea)), 
                  family = gaussian(), #gaussian error
                  data = .,
                  prior=set_prior("normal(0, 2)", class = "b"), #heirarchical prior-all slopes will use this
                  chains = 5, # nb of chains
                  iter = 5000, # nb of iterations, including burnin
                  warmup = 1000, # burnin
                  thin = 1) # no thinning

Insect_plant.brms <- imetaCent %>% 
  dplyr::filter(., type=="Plant") %>%
  brm(close~scale(log(globkm))+scale(log(envarea))+scale(log(globkm))*scale(log(envarea)), 
                  family = gaussian(), #gaussian error
                  data = .,
                  prior=set_prior("normal(0, 2)", class = "b"), #heirarchical prior-all slopes will use this
                  chains = 5, # nb of chains
                  iter = 5000, # nb of iterations, including burnin
                  warmup = 1000, # burnin
                  thin = 1) # no thinning


Avian_plant.brms <- bmetaCent %>% 
  dplyr::filter(., type=="Plant") %>%
  brm(close~scale(log(globkm))+scale(log(envarea))+scale(log(globkm))*scale(log(envarea)), 
                  family = gaussian(), #gaussian error
                  data = .,
                  prior=set_prior("normal(0, 2)", class = "b"), #heirarchical prior-all slopes will use this
                  chains = 5, # nb of chains
                  iter = 5000, # nb of iterations, including burnin
                  warmup = 1000, # burnin
                  thin = 1) # no thinning

Avian_visitor.brms <- bmetaCent %>% 
  dplyr::filter(., type=="Bird") %>%
  brm(close~scale(log(globkm))+scale(log(envarea))+scale(log(globkm))*scale(log(envarea)), 
                  family = gaussian(), #gaussian error
                  data = .,
                  prior=set_prior("normal(0, 2)", class = "b"), #heirarchical prior-all slopes will use this
                  chains = 5, # nb of chains
                  iter = 5000, # nb of iterations, including burnin
                  warmup = 1000, # burnin
                  thin = 1) # no thinning
```


Below, we use as_draws_df to extract posterior samples from the brms models we trained above. 
```{r}
samps <- as_draws_df(Insect_visitor.brms) %>% 
  dplyr::select(., b_Intercept, b_scalelogglobkm, b_scalelogenvarea, "b_scalelogglobkm:scalelogenvarea") %>%
  dplyr::mutate(type="Insect", net="Insect")
colnames(samps) <- c("intercept","geo","env","interaction","type","net")

temp <- as_draws_df(Insect_plant.brms) %>% 
  dplyr::select(., b_Intercept, b_scalelogglobkm, b_scalelogenvarea, "b_scalelogglobkm:scalelogenvarea") %>%
  dplyr::mutate(type="Plant", net="Insect")
colnames(temp) <- c("intercept","geo","env","interaction","type","net")
samps <- rbind(samps, temp)

temp <- as_draws_df(Avian_visitor.brms) %>% 
  dplyr::select(., b_Intercept, b_scalelogglobkm, b_scalelogenvarea, "b_scalelogglobkm:scalelogenvarea") %>%
  dplyr::mutate(type="Bird", net="Bird")
colnames(temp) <- c("intercept","geo","env","interaction","type","net")
samps <- rbind(samps, temp)

temp <- as_draws_df(Avian_plant.brms) %>% 
  dplyr::select(., b_Intercept, b_scalelogglobkm, b_scalelogenvarea, "b_scalelogglobkm:scalelogenvarea") %>%
  dplyr::mutate(type="Plant", net="Bird")
colnames(temp) <- c("intercept","geo","env","interaction","type","net")
samps <- rbind(samps, temp)


metaCentbayes <- pivot_longer(samps, cols = c("intercept","geo","env","interaction"))
metaCentbayes$combo <- paste(metaCentbayes$type, metaCentbayes$net, sep="-")

metaCentbayes$names <- c("Bird-Bird"="Avian Floral Visitor", "Plant-Bird"="Avian-Visited Plant", "Plant-Insect"="Insect-Visited Plant", "Insect-Insect"="Insect Floral Visitor")[metaCentbayes$combo]

metaCentbayes <- dplyr::rename(metaCentbayes, param=name)


#pdf(file="figs/leftbayesplot_main.pdf", width=7, height=11)
metaCentbayes %>% dplyr::filter(., param!="intercept") %>%
ggplot(., aes(x = value, y = names, fill=factor(stat(quantile)))) +
    stat_density_ridges(scale = 1.5,
    geom = "density_ridges_gradient",
    calc_ecdf = TRUE,
    quantiles = c(0.025, 0.975),
    rel_min_height=0.01
  )+
  theme_classic()+
  geom_vline(xintercept=0, col="red", linetype="dashed")+
  facet_wrap(~param, ncol=1,
    labeller = as_labeller(c(
      geo = "Geographic",
      env = "Niche Breadth",
      interaction = "Interaction Term"
    )))+
  scale_fill_manual(values = c("lightgrey", "dodgerblue", "lightgrey"))+ 
  guides(fill="none")+
  ylab("")+
  xlab("Coefficient value")+
  theme(axis.text.y=element_text(size=12), strip.text.x = element_text(size = 16))
#dev.off()

nrow(temp)

bayeClosesum <- metaCentbayes %>% 
  dplyr::group_by(., combo, param) %>% 
  dplyr::summarise(., leftail=sum(value<0)/nrow(temp), rightail=sum(value>0)/nrow(temp))%>%
  dplyr::mutate(pMCMC = 2*pmin(leftail, rightail)) #grab min tail and double, also drop groupings in case
```

Repeat for z-standardized version

```{r}
Insect_visitor.brms.z <- imetaCent %>% 
  dplyr::filter(., type=="Insect") %>%
  brm(close.z~scale(log(globkm))+scale(log(envarea))+scale(log(globkm))*scale(log(envarea)), 
                  family = gaussian(), #gaussian error
                  data = .,
                  prior=set_prior("normal(0, 2)", class = "b"), #heirarchical prior-all slopes will use this
                  chains = 5, # nb of chains
                  iter = 5000, # nb of iterations, including burnin
                  warmup = 1000, # burnin
                  thin = 1) # no thinning

Insect_plant.brms.z <- imetaCent %>% 
  dplyr::filter(., type=="Plant") %>%
  brm(close.z~scale(log(globkm))+scale(log(envarea))+scale(log(globkm))*scale(log(envarea)), 
                  family = gaussian(), #gaussian error
                  data = .,
                  prior=set_prior("normal(0, 2)", class = "b"), #heirarchical prior-all slopes will use this
                  chains = 5, # nb of chains
                  iter = 5000, # nb of iterations, including burnin
                  warmup = 1000, # burnin
                  thin = 1) # no thinning


Avian_plant.brms.z <- bmetaCent %>% 
  dplyr::filter(., type=="Plant") %>%
  brm(close.z~scale(log(globkm))+scale(log(envarea))+scale(log(globkm))*scale(log(envarea)), 
                  family = gaussian(), #gaussian error
                  data = .,
                  prior=set_prior("normal(0, 2)", class = "b"), #heirarchical prior-all slopes will use this
                  chains = 5, # nb of chains
                  iter = 5000, # nb of iterations, including burnin
                  warmup = 1000, # burnin
                  thin = 1) # no thinning

Avian_visitor.brms.z <- bmetaCent %>% 
  dplyr::filter(., type=="Bird") %>%
  brm(close.z~scale(log(globkm))+scale(log(envarea))+scale(log(globkm))*scale(log(envarea)), 
                  family = gaussian(), #gaussian error
                  data = .,
                  prior=set_prior("normal(0, 2)", class = "b"), #heirarchical prior-all slopes will use this
                  chains = 5, # nb of chains
                  iter = 5000, # nb of iterations, including burnin
                  warmup = 1000, # burnin
                  thin = 1) # no thinning

samps <- as_draws_df(Insect_visitor.brms.z) %>% 
  dplyr::select(., b_Intercept, b_scalelogglobkm, b_scalelogenvarea, "b_scalelogglobkm:scalelogenvarea") %>%
  dplyr::mutate(type="Insect", net="Insect")
colnames(samps) <- c("intercept","geo","env","interaction","type","net")

temp <- as_draws_df(Insect_plant.brms.z) %>% 
  dplyr::select(., b_Intercept, b_scalelogglobkm, b_scalelogenvarea, "b_scalelogglobkm:scalelogenvarea") %>%
  dplyr::mutate(type="Plant", net="Insect")
colnames(temp) <- c("intercept","geo","env","interaction","type","net")
samps <- rbind(samps, temp)

temp <- as_draws_df(Avian_visitor.brms.z) %>% 
  dplyr::select(., b_Intercept, b_scalelogglobkm, b_scalelogenvarea, "b_scalelogglobkm:scalelogenvarea") %>%
  dplyr::mutate(type="Bird", net="Bird")
colnames(temp) <- c("intercept","geo","env","interaction","type","net")
samps <- rbind(samps, temp)

temp <- as_draws_df(Avian_plant.brms.z) %>% 
  dplyr::select(., b_Intercept, b_scalelogglobkm, b_scalelogenvarea, "b_scalelogglobkm:scalelogenvarea") %>%
  dplyr::mutate(type="Plant", net="Bird")
colnames(temp) <- c("intercept","geo","env","interaction","type","net")
samps <- rbind(samps, temp)


metaCentbayes.z <- pivot_longer(samps, cols = c("intercept","geo","env","interaction"))
metaCentbayes.z$combo <- paste(metaCentbayes.z$type, metaCentbayes.z$net, sep="-")

metaCentbayes.z$names <- c("Bird-Bird"="Avian Floral Visitor", "Plant-Bird"="Avian-Visited Plant", "Plant-Insect"="Insect-Visited Plant", "Insect-Insect"="Insect Floral Visitor")[metaCentbayes.z$combo]

metaCentbayes.z <- dplyr::rename(metaCentbayes.z, param=name)

```


```{r}

#pdf(file="figs/rightbayesplot_main.pdf", width=5, height=11)
metaCentbayes.z %>% dplyr::filter(., param!="intercept") %>%
ggplot(., aes(x = value, y = names, fill=factor(stat(quantile)))) +
    stat_density_ridges(scale = 1,
    geom = "density_ridges_gradient",
    calc_ecdf = TRUE,
    quantiles = c(0.025, 0.975),
    rel_min_height=0.01
  )+
  theme_classic()+
  geom_vline(xintercept=0, col="red", linetype="dashed")+
  facet_wrap(~param, ncol=1,
    labeller = as_labeller(c(
      geo = "Geographic Range",
      env = "Environmental Range",
      interaction = "Interaction"
    )))+
  scale_fill_manual(values = c("lightgrey", "dodgerblue", "lightgrey"))+ 
  guides(fill="none")+
  ylab("")+
  xlab("Coefficient value")+
  theme(axis.text.y=element_text(size=12), strip.text.x = element_text(size = 16))
#dev.off()



bayeZsum <- metaCentbayes.z %>% 
  dplyr::group_by(., combo, param) %>% 
  dplyr::summarise(., leftail=sum(value<0)/nrow(temp), rightail=sum(value>0)/nrow(temp))%>%
  dplyr::mutate(pMCMC = 2*pmin(leftail, rightail)) #grab min tail and double, also drop groupings in case
```


Plotting the effects of range size on local centrality
```{r}
#Sig in geo raw: Insect Pollinators, Insect Pollinated Plants
clrs <- c("#ad85ed", "#02b593")
  
geoRngLocal <- compositeLocal %>% 
  ggplot(., aes(x=scale(log(globkm)), y=close, col=net))+
  geom_point(alpha=0.4)+
  geom_smooth(method="lm", data=dplyr::filter(compositeLocal, net=="Insect"))+ #Remove insignificant coefficients from the lm data
  facet_wrap(~type, labeller = labeller(type = c("Floral Visitors", "Plants")))+
  theme_classic()+
  xlab("Scaled Log Geographic Area")+
  ylab("Closeness Centrality in \n Local Web")+guides(col=guide_legend(title="MetaNetwork"))+
  scale_color_manual(labels = c("Avian-Plant", "Insect-Plant"), values = clrs)+
  theme(legend.position=c(0.15,.85), guide_legend(override.aes=list(fill=NA)))+
       theme(strip.text.x = element_text(size = 14))

#Sig in env raw: Insect Pollinated Plants
envRngLocal <- compositeLocal %>% 
  ggplot(., aes(x=scale(log(envarea)), y=close, col=net))+
  geom_point(alpha=0.4)+
  geom_smooth(method="lm", data=dplyr::filter(compositeLocal, type=="Plant" & net=="Insect"))+
  facet_wrap(~type)+
  theme_classic()+
  xlab("Scaled Log Environmental Area")+
  ylab("Closeness Centrality in \n Local Web")+guides(col="none")+
  scale_color_manual(labels = c("Avian-Plant", "Insect-Plant"), values = clrs)+
       theme(strip.text.x = element_text(size = 14))

#Sig in geo.z: 
geoRngLocal.z <- compositeLocal %>% 
  ggplot(., aes(x=scale(log(globkm)), y=z.close, col=net))+
  geom_point(alpha=0.4)+
  #geom_smooth(method="lm", data=dplyr::filter(compositeLocal, type=="Plant" & net=="Bird"))+ #no sig relationships
  facet_wrap(~type)+
  theme_classic()+
  xlab("Scaled Log Geographic Area")+
  ylab("Closeness Centrality in \n Local Web (Z-transformed)")+guides(col="none")+
  scale_color_manual(labels = c("Avian-Plant", "Insect-Plant"), values = clrs)+
       theme(strip.text.x = element_text(size = 14))

#Sig in env.z: Insect Pollinated Plants
envRngLocal.z <- compositeLocal %>% 
  ggplot(., aes(x=scale(log(envarea)), y=z.close, col=net))+
  geom_point(alpha=0.4)+
  geom_smooth(method="lm", data=dplyr::filter(compositeLocal, type=="Plant" & net=="Insect"))+
  facet_wrap(~type)+
  theme_classic()+
  xlab("Scaled Log Environmental Area")+
  ylab("Closeness Centrality in \n Local Web (Z-transformed)")+guides(col="none")+
  scale_color_manual(labels = c("Avian-Plant", "Insect-Plant"), values = clrs)+
       theme(strip.text.x = element_text(size = 14))

#pdf(file="cleanFigs/LocalCentralityPlot.pdf", width=10, height=8)
grid.arrange(geoRngLocal, geoRngLocal.z, envRngLocal, envRngLocal.z, nrow=2)
#dev.off()

#dev.off()
#pdf(file="cleanFigs/LocalCentralityPlot_Small.pdf", width=10, height=8)
grid.arrange(geoRngLocal.z, envRngLocal.z, nrow=2)
#dev.off()
```

#Summary information
```{r}
cor.test(compositeMeta$globkm, compositeMeta$envarea)

imetaCent <- localiCent %>% 
  group_by(., node) %>% 
  dplyr::summarise(., meanLocalclose=mean(close), sdLocalclose=sd(close)) %>% #grab average and sd of closeness across sites with multiple species. 
  dplyr::left_join(imetaCent, ., by="node")

cor.test(imetaCent$close, imetaCent$meanLocalclose)

bmetaCent <- localbCent %>% 
  group_by(., node) %>% 
  dplyr::summarise(., meanLocalclose=mean(close), sdLocalclose=sd(close)) %>% #grab average and sd of closeness across sites with multiple species. 
  dplyr::left_join(bmetaCent, ., by="node")

cor.test(bmetaCent$close, bmetaCent$meanLocalclose)
```

Now performing Bayesian version the local web plotting. 

```{r}
Insect_visitor.brms.local <- localiCent %>% 
  dplyr::filter(., type=="Insect") %>%
  brm(z.close~scale(log(globkm))+scale(log(envarea))+scale(log(globkm))*scale(log(envarea)), 
                  family = gaussian(), #gaussian error
                  data = .,
                  prior=set_prior("normal(0, 2)", class = "b"), #heirarchical prior-all slopes will use this
                  chains = 5, # nb of chains
                  iter = 5000, # nb of iterations, including burnin
                  warmup = 1000, # burnin
                  thin = 1) # no thinning

Insect_plant.brms.local <- localiCent %>% 
  dplyr::filter(., type=="Plant") %>%
  brm(z.close~scale(log(globkm))+scale(log(envarea))+scale(log(globkm))*scale(log(envarea)), 
                  family = gaussian(), #gaussian error
                  data = .,
                  prior=set_prior("normal(0, 2)", class = "b"), #heirarchical prior-all slopes will use this
                  chains = 5, # nb of chains
                  iter = 5000, # nb of iterations, including burnin
                  warmup = 1000, # burnin
                  thin = 1) # no thinning


Avian_plant.brms.local <- localbCent %>% 
  dplyr::filter(., type=="Plant") %>%
  brm(z.close~scale(log(globkm))+scale(log(envarea))+scale(log(globkm))*scale(log(envarea)), 
                  family = gaussian(), #gaussian error
                  data = .,
                  prior=set_prior("normal(0, 2)", class = "b"), #heirarchical prior-all slopes will use this
                  chains = 5, # nb of chains
                  iter = 5000, # nb of iterations, including burnin
                  warmup = 1000, # burnin
                  thin = 1) # no thinning

Avian_visitor.brms.local <- localbCent %>% 
  dplyr::filter(., type=="Bird") %>%
  brm(z.close~scale(log(globkm))+scale(log(envarea))+scale(log(globkm))*scale(log(envarea)), 
                  family = gaussian(), #gaussian error
                  data = .,
                  prior=set_prior("normal(0, 2)", class = "b"), #heirarchical prior-all slopes will use this
                  chains = 5, # nb of chains
                  iter = 5000, # nb of iterations, including burnin
                  warmup = 1000,
      thin=1) # burnin
     


samps <- as_draws_df(Insect_visitor.brms.local) %>% 
  dplyr::select(., b_Intercept, b_scalelogglobkm, b_scalelogenvarea, "b_scalelogglobkm:scalelogenvarea") %>%
  dplyr::mutate(type="Insect", net="Insect")
colnames(samps) <- c("intercept","geo","env","interaction","type","net")

temp <- as_draws_df(Insect_plant.brms.local) %>% 
  dplyr::select(., b_Intercept, b_scalelogglobkm, b_scalelogenvarea, "b_scalelogglobkm:scalelogenvarea") %>%
  dplyr::mutate(type="Plant", net="Insect")
colnames(temp) <- c("intercept","geo","env","interaction","type","net")
samps <- rbind(samps, temp)

temp <- as_draws_df(Avian_visitor.brms.local) %>% 
  dplyr::select(., b_Intercept, b_scalelogglobkm, b_scalelogenvarea, "b_scalelogglobkm:scalelogenvarea") %>%
  dplyr::mutate(type="Bird", net="Bird")
colnames(temp) <- c("intercept","geo","env","interaction","type","net")
samps <- rbind(samps, temp)

temp <- as_draws_df(Avian_plant.brms.local) %>% 
  dplyr::select(., b_Intercept, b_scalelogglobkm, b_scalelogenvarea, "b_scalelogglobkm:scalelogenvarea") %>%
  dplyr::mutate(type="Plant", net="Bird")
colnames(temp) <- c("intercept","geo","env","interaction","type","net")
samps <- rbind(samps, temp)


localCentbayes <- pivot_longer(samps, cols = c("intercept","geo","env","interaction"))
localCentbayes$combo <- paste(localCentbayes$type, localCentbayes$net, sep="-")

localCentbayes$names <- c("Bird-Bird"="Avian Floral Visitor", "Plant-Bird"="Avian-Visited Plant", "Plant-Insect"="Insect-Visited Plant", "Insect-Insect"="Insect Floral Visitor")[localCentbayes$combo]

localCentbayes <- dplyr::rename(localCentbayes, param=name) 
      
```

And creating plots

```{r}
#pdf(file="figs/local_bayesplot.pdf", width=7, height=11)
localCentbayes %>% dplyr::filter(., param!="intercept") %>%
ggplot(., aes(x = value, y = names, fill=factor(stat(quantile)))) +
    stat_density_ridges(scale = 1,
    geom = "density_ridges_gradient",
    calc_ecdf = TRUE,
    quantiles = c(0.025, 0.975),
    rel_min_height=0.01
  )+
  theme_classic()+
  geom_vline(xintercept=0, col="red", linetype="dashed")+
  facet_wrap(~param, ncol=1,
    labeller = as_labeller(c(
      geo = "Geographic Range",
      env = "Environmental Range",
      interaction = "Interaction"
    )))+
  scale_fill_manual(values = c("lightgrey", "dodgerblue", "lightgrey"))+ 
  guides(fill="none")+
  ylab("")+
  xlab("Coefficient value")+
  theme(axis.text.y=element_text(size=12), strip.text.x = element_text(size = 16))
#dev.off()


```
pMCMC

```{r}
bayeLocsum <- localCentbayes %>% 
  dplyr::group_by(., combo, param) %>% 
  dplyr::summarise(., leftail=sum(value<0)/5000, rightail=sum(value>0)/5000)%>%
  dplyr::mutate(pMCMC = 2*pmin(leftail, rightail)) #grab min tail and double, also drop groupings in case


bayeLocsum %>% dplyr::filter(., param!="intercept")
```



Metaweb connectance
```{r}
nlinks <- Insectweb %>% select(., species1, species2) %>% unique() %>% nrow() #number of links
nlinks/(length(unique(Insectweb$species1))*length(unique(Insectweb$species2))) #divided by total potential

nlinks <- Birdweb %>% select(., species1, species2) %>% unique() %>% nrow() #number of links
nlinks/(length(unique(Birdweb$species1))*length(unique(Birdweb$species2))) #divided by total potential

rm(nlinks) #housekeeping
```
## Supplement

Connectance of local webs
```{r}
iCon <- NULL

for(i in unique(Insectweb$site_index)){
  tempweb <- dplyr::filter(Insectweb, site_index==i)
  nlinks <- tempweb %>% select(., species1, species2) %>% unique() %>% nrow() #number of links
  Ctemp <- nlinks/(length(unique(tempweb$species1))*length(unique(tempweb$species2))) #divided by total potential
  iCon <- rbind(iCon, Ctemp)
}

bCon <- NULL
for(i in unique(Birdweb$site_index)){
  tempweb <- dplyr::filter(Birdweb, site_index==i)
  nlinks <- tempweb %>% select(., species1, species2) %>% unique() %>% nrow() #number of links
  Ctemp <- nlinks/(length(unique(tempweb$species1))*length(unique(tempweb$species2))) #divided by total potential
  bCon <- rbind(bCon, Ctemp)
}

mean(iCon)
mean(bCon)

iConplot <- ggplot() + aes(iCon)+ 
  geom_histogram(colour="black", fill="#00896f")+
  ylab("Frequency")+
  xlab("Connectance (Insect-Plant Network)")+theme_classic()

bConplot <- ggplot() + aes(bCon)+ 
  geom_histogram(colour="black", fill="#845ec2")+
  ylab("Frequency")+
  xlab("Connectance (Avian-Plant Network)")+theme_classic()

#pdf(file="cleanFigs/LocalConnectanceDistributions.pdf", width=10, height=8)
grid.arrange(iConplot, bConplot, nrow=1)
#dev.off()
rm(iCon, bCon, iConplot, bConplot)
```

Range sizes
```{r}
median(imetaCent$globkm, na.rm=T)
range(imetaCent$globkm, na.rm=T)

median(bmetaCent$globkm, na.rm=T)
range(bmetaCent$globkm, na.rm=T)
```


Supplemental plots
```{r}
compositeLocal <- compositeLocal %>% 
  dplyr::group_by(., node, net) %>% 
  dplyr::mutate(., nsites=n()) #Count number of unique sites

bRepPlot <- compositeLocal %>% dplyr::filter(., net=="Bird") %>% dplyr::filter(., nsites>5) %>%
ggplot(aes(x=factor(node, levels=unique(node[order(nsites, decreasing = T)])), y=close,
           fill=nsites), data=.)+
  geom_boxplot(outlier.shape = NA)+ 
  scale_fill_continuous(name = "Number of Sites")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 305, vjust = 0.5, hjust=0))+
  ylab("Local Closeness")+
  xlab("Species (Avian Network)")+
  geom_point(aes(x=factor(node, levels=unique(node[order(nsites, decreasing = T)])), y=close), size=1.5)

bRepPlot.z <- compositeLocal %>% dplyr::filter(., net=="Bird") %>% dplyr::filter(., nsites>5) %>%
ggplot(aes(x=factor(node, levels=unique(node[order(nsites, decreasing = T)])), y=z.close,
           fill=nsites), data=.)+
  geom_boxplot(outlier.shape = NA)+ 
  scale_fill_continuous(name = "Number of Sites")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 305, vjust = 0.5, hjust=0))+
  ylab("Local Closeness \n (Z-transformed)")+
  xlab("Species (Avian Network)")+
  geom_point(aes(x=factor(node, levels=unique(node[order(nsites, decreasing = T)])), y=z.close), size=1.5)+
  geom_hline(yintercept=1.96, linetype='dotted', col = 'red')+
  geom_hline(yintercept=-1.96, linetype='dotted', col = 'red')

iRepPlot <- compositeLocal %>% dplyr::filter(., net=="Insect") %>% dplyr::filter(., nsites>10) %>%
ggplot(aes(x=factor(node, levels=unique(node[order(nsites, decreasing = T)])), y=close,
           fill=log(nsites)), data=.)+
  geom_boxplot(outlier.shape = NA)+ 
  scale_fill_continuous(name = "Number of Sites (Log)")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 305, vjust = 0.5, hjust=0))+
  ylab("Local Closeness")+
  xlab("Species (Insect Network)")+
  geom_point(aes(x=factor(node, levels=unique(node[order(nsites, decreasing = T)])), y=close), size=1.5)

iRepPlot.z <- compositeLocal %>% dplyr::filter(., net=="Insect") %>% dplyr::filter(., nsites>10) %>%
ggplot(aes(x=factor(node, levels=unique(node[order(nsites, decreasing = T)])), y=z.close,
           fill=log(nsites)), data=.)+
  geom_boxplot(outlier.shape = NA)+ 
  scale_fill_continuous(name = "Number of Sites (Log)")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 305, vjust = 0.5, hjust=0))+
  ylab("Local Closeness \n (Z-transformed)")+
  xlab("Species (Insect Network)")+
  geom_point(aes(x=factor(node, levels=unique(node[order(nsites, decreasing = T)])), y=z.close), size=1.5)+
  geom_hline(yintercept=1.96, linetype='dotted', col = 'red')+
  geom_hline(yintercept=-1.96, linetype='dotted', col = 'red')

#pdf(file="cleanFigs/Local_Centrality_Distributions.pdf", width=10, height=8)
grid.arrange(bRepPlot, bRepPlot.z, iRepPlot, iRepPlot.z, nrow=2)
#dev.off()
```


Related question: Is # of coocuring species related to geographic range size? What about centrality?
```{r}
#Create species-by-site table
species1_by_site <- Birdweb %>%
  distinct(site_index, species1)

#Use above to find intraguild coocurences
Birdweb <- species1_by_site %>%
  inner_join(species1_by_site, by = "site_index") %>% #join all cooccurences by the "site_index" key (one to many relationship is actually expected and cool)
  dplyr::filter(species1.x != species1.y) %>%  # remove self-pairings
  dplyr::distinct(species1.x, species1.y) %>%  # remove duplicates (coocure at multiple sites)
  dplyr::group_by(species1.x) %>%
  dplyr::summarise(n_intraaguildCooccur_sp1 = n(), .groups = "drop") %>% #count the number of coccurences
  dplyr::rename(species1 = species1.x) %>%
  left_join(Birdweb, ., by="species1")

#Recreate clean species-by-site table
species1_by_site <- Birdweb %>%
  distinct(site_index, species1)
#Find extraguild coocurences
Birdweb <- dplyr::select(Birdweb, species2, site_index) %>%
  unique() %>%
  left_join(species1_by_site, ., by="site_index") %>%
  unique() %>% 
  group_by(., species1) %>%
  dplyr::summarise(n_extraguildCooccur_sp1 = n(), .groups = "drop") %>%
  left_join(Birdweb, ., by=c("species2"))


####NOw recreate for species 2
#Create species-by-site table
species2_by_site <- Birdweb %>%
  distinct(site_index, species2)

#Use above to find intraguild coocurences
Birdweb <- species2_by_site %>%
  inner_join(species2_by_site, by = "site_index") %>% #join all cooccurences by the "site_index" key (one to many relationship is actually expected and cool)
  dplyr::filter(species2.x != species2.y) %>%  # remove self-pairings
  dplyr::distinct(species2.x, species2.y) %>%  # remove duplicates (coocure at multiple sites)
  dplyr::group_by(species2.x) %>%
  dplyr::summarise(n_intraaguildCooccur_sp2 = n(), .groups = "drop") %>% #count the number of coccurences
  dplyr::rename(species2 = species2.x) %>%
  left_join(Birdweb, ., by="species2")


#Recreate clean species-by-site table
species2_by_site <- Birdweb %>%
  distinct(site_index, species2)
#Find extraguild coocurences
Birdweb <- dplyr::select(Birdweb, species1, site_index) %>%
  unique() %>%
  left_join(species2_by_site, ., by="site_index") %>%
  unique() %>% 
  group_by(., species2) %>%
  dplyr::summarise(n_extraguildCooccur_sp2 = n(), .groups = "drop") %>%
  left_join(Birdweb, ., by=c("species2"))

###################Repeat all of above for insect Web

#Create species-by-site table
species1_by_site <- Insectweb %>%
  distinct(site_index, species1)

#Use above to find intraguild coocurences
Insectweb <- species1_by_site %>%
  inner_join(species1_by_site, by = "site_index") %>% #join all cooccurences by the "site_index" key (one to many relationship is actually expected and cool)
  dplyr::filter(species1.x != species1.y) %>%  # remove self-pairings
  dplyr::distinct(species1.x, species1.y) %>%  # remove duplicates (coocure at multiple sites)
  dplyr::group_by(species1.x) %>%
  dplyr::summarise(n_intraaguildCooccur_sp1 = n(), .groups = "drop") %>% #count the number of coccurences
  dplyr::rename(species1 = species1.x) %>%
  left_join(Insectweb, ., by="species1")

#Recreate clean species-by-site table
species1_by_site <- Insectweb %>%
  distinct(site_index, species1)
#Find extraguild coocurences
Insectweb <- dplyr::select(Insectweb, species2, site_index) %>%
  unique() %>%
  left_join(species1_by_site, ., by="site_index") %>%
  unique() %>% 
  group_by(., species1) %>%
  dplyr::summarise(n_extraguildCooccur_sp1 = n(), .groups = "drop") %>%
  left_join(Insectweb, ., by=c("species1"))


####NOw recreate for species 2
#Create species-by-site table
species2_by_site <- Insectweb %>%
  distinct(site_index, species2)

#Use above to find intraguild coocurences
Insectweb <- species2_by_site %>%
  inner_join(species2_by_site, by = "site_index") %>% #join all cooccurences by the "site_index" key (one to many relationship is actually expected and cool)
  dplyr::filter(species2.x != species2.y) %>%  # remove self-pairings
  dplyr::distinct(species2.x, species2.y) %>%  # remove duplicates (coocure at multiple sites)
  dplyr::group_by(species2.x) %>%
  dplyr::summarise(n_intraaguildCooccur_sp2 = n(), .groups = "drop") %>% #count the number of coccurences
  dplyr::rename(species2 = species2.x) %>%
  left_join(Insectweb, ., by="species2")


#Recreate clean species-by-site table
species2_by_site <- Insectweb %>%
  distinct(site_index, species2)
#Find extraguild coocurences
Insectweb <- dplyr::select(Insectweb, species1, site_index) %>%
  unique() %>%
  left_join(species2_by_site, ., by="site_index") %>%
  unique() %>% 
  group_by(., species2) %>%
  dplyr::summarise(n_extraguildCooccur_sp2 = n(), .groups = "drop") %>%
  left_join(Insectweb, ., by=c("species2"))

rm(species1_by_site, species2_by_site) #cleanup
```

Plotting based on the above
```{r}
compositeMeta2 <- compositeMeta
compositeMeta2 <- rbind(imetaCent, bmetaCent) %>% dplyr::filter(., is.na(envarea)==F)
compositeMeta2$type[compositeMeta2$type %in% c("Insect", "Bird")] <- "Floral Visitor"

compositeMeta2 <- data.frame(node=c(Insectweb$species1, Insectweb$species2, Birdweb$species1, Birdweb$species2),
intra=c(Insectweb$n_intraaguildCooccur_sp1, Insectweb$n_intraaguildCooccur_sp2, Birdweb$n_intraaguildCooccur_sp1, Birdweb$n_intraaguildCooccur_sp2), extra=c(Insectweb$n_extraguildCooccur_sp1, Insectweb$n_extraguildCooccur_sp2, Birdweb$n_extraguildCooccur_sp1, Birdweb$n_extraguildCooccur_sp2)) %>% #assemble our resultant data
unique() %>%
  left_join(compositeMeta2,., by="node")


#pdf(file="cleanFigs/Cooccurence_vs_GeographicRange.pdf", width=10, height=8)
compositeMeta2 %>% 
  ggplot(., aes(x=log(globkm), y=log(extra), col=net))+
  geom_point(alpha=0.7)+
  geom_smooth(method="lm") + 
  #geom_smooth(method="lm", data=dplyr::filter(compositeMeta, type!="Floral Visitor" | net=="Insect"))+ #Remove insignificant coefficients from the lm data
  facet_wrap(~type, labeller = labeller(type = c("Floral Visitors", "Plants")))+
  theme_classic()+
  ylab("Number of Extraguild Cooccuring Species (log)")+
  xlab("Scaled Log Geographic Area")+guides(col=guide_legend(title="MetaNetwork"))+
  scale_color_manual(labels = c("Avian-Plant", "Insect-Plant"), values = c("red", "black"))+
  theme(legend.position=c(0.15,.85), guide_legend(override.aes=list(fill=NA)))+
       theme(strip.text.x = element_text(size = 14))
#dev.off()
```
Needs a site by species matrix
```{r, eval==F}
#cycle across insect pollinators
partition <- NULL

#first for pollinators
for(spID in 1:length(unique(Insectweb$species2))){
temp <- dplyr::filter(Insectweb, species2==unique(Insectweb$species2)[spID]) #find interactions
com <-  as.data.frame.matrix(xtabs(formula=~species1+site_index, data=temp)) #Create community matrix
tempdat <- data.frame(species=unique(Insectweb$species2)[spID],turnover=nestedbetasor(com)[1],nestedness=nestedbetasor(com)[2],sorenson=nestedbetasor(com)[3], nsites=ncol(com), ncooc=nrow(com), type="Insect", net="Insect") #calculate nestedness + turnover partition according to Baselga 2012
  if(spID%%50==0){
    print(paste("done with", spID))
  }
partition <- rbind(partition, tempdat)
}

#now for plants
for(spID in 1:length(unique(Insectweb$species1))){
temp <- dplyr::filter(Insectweb, species1==unique(Insectweb$species1)[spID]) #find interactions
com <-  as.data.frame.matrix(xtabs(formula=~species2+site_index, data=temp)) #Create community matrix
tempdat <- c(species=unique(Insectweb$species1)[spID],turnover=nestedbetasor(com)[1],nestedness=nestedbetasor(com)[2],sorenson=nestedbetasor(com)[3], nsites=ncol(com), ncooc=nrow(com), type="Plant", net="Insect") #calculate nestedness + turnover partition according to Baselga 2012
  if(spID%%50==0){
    print(paste("done with", spID))
  }
partition <- rbind(partition, tempdat)
}

#repeat for avian pollinators
for(spID in 1:length(unique(Birdweb$species2))){
  temp <- dplyr::filter(Birdweb, species2==unique(Birdweb$species2)[spID]) #find interactions
  com <-  as.data.frame.matrix(xtabs(formula=~species1+site_index, data=temp)) #Create community matrix
  tempdat <- data.frame(species=unique(Birdweb$species2)[spID],turnover=nestedbetasor(com)[1],nestedness=nestedbetasor(com)[2],sorenson=nestedbetasor(com)[3], nsites=ncol(com), ncooc=nrow(com), type="Bird", net="Bird") #calculate nestedness + turnover partition according to Baselga 2012
    if(spID%%50==0){
      print(paste("done with", spID))
    }
  partition <- rbind(partition, tempdat)
}

#And finally for avian pollinated plants
for(spID in 1:length(unique(Birdweb$species1))){
temp <- dplyr::filter(Birdweb, species1==unique(Birdweb$species1)[spID]) #find interactions
com <-  as.data.frame.matrix(xtabs(formula=~species2+site_index, data=temp)) #Create community matrix
tempdat <- c(species=unique(Birdweb$species1)[spID],turnover=nestedbetasor(com)[1],nestedness=nestedbetasor(com)[2],sorenson=nestedbetasor(com)[3], nsites=ncol(com), ncooc=nrow(com), type="Plant", net="Bird") #calculate nestedness + turnover partition according to Baselga 2012
  if(spID%%50==0){
    print(paste("done with", spID))
  }
partition <- rbind(partition, tempdat)
}
partition$turnover <- as.numeric(partition$turnover)
partition$nestedness <- as.numeric(partition$nestedness)
partition$sorenson <- as.numeric(partition$sorenson)
partition$nsites <- as.numeric(partition$nsites)
partition$ncooc <- as.numeric(partition$ncooc)
#save(partition, file="Betadiverpartition.RDA")
```

Adding our results of our beta diversity partitioning to our existing metawebs

```{r}
load(file="Betadiverpartition.RDA")
partition <- dplyr::filter(partition, nsites>1) %>%
  dplyr::filter(., is.na(sorenson)==F)

imetaCent <- partition %>% dplyr::rename(., node=species) %>% 
  dplyr::filter(., net=="Insect") %>%
  left_join(imetaCent, ., by=c("node", "type", "net"))

bmetaCent <- partition %>% dplyr::rename(., node=species) %>% 
  dplyr::filter(., net=="Bird") %>%
  left_join(bmetaCent, ., by=c("node", "type", "net"))
```

Let's do some plotting
```{r}

bmetaCent %>% 
  ggplot(., aes(x=scale(log(globkm)), y=sorenson))+
  geom_point(alpha=0.4)+
  theme_classic()+
  xlab("Scaled Log Geographic Area")

bmetaCent %>% 
  ggplot(., aes(x=log(nsites), y=turnover))+
  geom_point(alpha=0.4)+
  theme_classic()+
  xlab("Number of Sites (log)")

bmetaCent %>% 
  ggplot(., aes(x=log(globkm), y=turnover))+
  geom_point(alpha=0.4)+
  theme_classic()+
  xlab("Number of Sites (log)")

bmetaCent %>% 
  ggplot(., aes(x=log(scale(envarea)), y=turnover))+
  geom_point(alpha=0.4)+
  theme_classic()+
  xlab("Scaled")

summary(lm(turnover~log(scale(globkm)), data=bmetaCent))
summary(lm(turnover~log(scale(envarea)), data=bmetaCent))
summary(lm(turnover~log(nsites), data=bmetaCent))
summary(lm(sorenson~log(nsites), data=bmetaCent))

hist(imetaCent$turnover/imetaCent$sorenson)
```

#New aside:
Comparing to BIEN
```{r}

```

